\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{siunitx}
\pagestyle{plain}
\renewcommand{\o}{\theta}
\newcommand{\w}{\omega}
\newcommand{\p}{\phi}
\begin{document}

\begin{center}
\Large Math-19 Practice Exam \#5
\end{center}

\vspace{0.5in}

\begin{enumerate}

\item Consider the angle $\o=-55^{\circ}$.
  \begin{enumerate}
  \item Convert to radians (leave the answer reduced and in terms of $\pi$).

  \item Find a coterminal angle in the interval $[0,2\pi]$.
  \end{enumerate}

\item Consider the trigonometric function:
  \[f(t)=3\sin(4t-\pi)\]
  \begin{enumerate}
  \item What is the amplitude?

    $A=$

  \item What is the angular frequency?

    $\w=$

  \item What is the period?

    $T=$
    
  \item What is the horizontal translation?

    $b=$\hspace{1in}to the:
    
  \item What is the phase angle?

    $\p=$

  \item Sketch one period of the graph from $[b,b+T]$. Be sure to label the
    four key $t$ values and use dotted lines to indicate the amplitude.

    \begin{tikzpicture}[scale=0.75]
      \draw (-5,0) -- (5,0);
      \draw (0,-5) -- (0,5);
    \end{tikzpicture}
  \end{enumerate}

\item Consider the trigonometric function:
  \[f(t)=-2\tan\left[\pi\left(t+\frac{1}{2}\right)\right]\]
  \begin{enumerate}
  \item What is the angular frequency?

    $\w=$

  \item What is the period?

    $T=$
    
  \item What is the horizontal translation?

    $b=$\hspace{1in}to the:
    
  \item Sketch one period of the graph from
    $\left(b-\frac{T}{2},b+\frac{T}{2}\right)$. Be sure to show the asymptotes
    at the ends of the interval and label the zero.

    \vspace{0.25in}

    \begin{tikzpicture}
      \draw (-5,0) -- (5,0);
      \draw (0,-5) -- (0,5);
    \end{tikzpicture}
  \end{enumerate}

\item Evaluate the following expressions:
  \[\sin^{-1}\left(\sin\frac{2\pi}{3}\right)\]

\item Evaluate the following expressions:
  \[\cos\left(\cot^{-1}\frac{1}{2}\right)\]

\item Rewrite the following expression in terms of $x$:
  \[\cot\left(\sin^{-1}\frac{x}{4}\right)\]

\item The typical windmill used for electricity generation has blades that are
  $\SI{116}{ft}$ long and turn at about $\SI{20}{rpm}$. How fast are the
  tips of the blades moving (in mph)?

\item A guy (support) wire is connected from the ground to the top of a pole.
  The end of the guy wire is $\SI{10}{feet}$ from the pole and makes an angle
  of elevation of $70^{\circ}$ with the ground.  How tall is the pole (to the
  nearest tenth of a foot)?

\item Two people are walking in the park when they see a bird fly by. At some
  point in time, the angle of elevation from the first person to the bird is
  $50^{\circ}$ and the angle of elevation from the second person to the bird is
  $75^{\circ}$. The distance between the two people is $\SI{50}{ft}$. What is
  the distance between the bird and the second person (to the nearest tenth
  of a foot)?

\item A particle undergoes damped harmonic motion in one dimension about the
  equilibrium position $x=0$. Let $x(t)$ denote the particle's position at
  time $t$. At $f(0)=10$ the particle is at its right-most position for the
  first cycle. At $f(1)=-7$ the particle reaches its left-most position for the
  first cycle. Recall that the equation for this type of motion is:
  \[f(t)=Ae^{-kt}\cos\w t\]
  \begin{enumerate}
  \item Identify the following values:
    \[A=\]
    \[T=\]
    \[\w=\]
  \item Calculate $k$. Round your answer to two significant digits.
  \end{enumerate}

\end{enumerate}

\end{document}
