\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\renewcommand{\o}{\theta}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Homework \#7
\end{center}

\vspace{0.5in}

\underline{Reading}

Please read sections 6.1 through 6.3 and 5.1 through 5.3 and do all concept
problems in the posted sections on web\-assign.

\underline{Problems}

\begin{enumerate}
\item A blu-ray disk has a diameter of $12cm$. The track of recorded
information on the disk spirals in from the outside toward the center. A blu-ray
player must make sure that the track passing under the optical reader stays at
a constant linear speed, so the motor will vary from 200 to 500 rpm, depending
on where the disk is being read.
\begin{enumerate}
\item Which angular speed is used for the  part of the track on the outer rim
of the disk? Why?
\item What is the linear speed of the outer track in cm/s?
\item What is the distance from the center of the disk for the innermost part
of the track?
\end{enumerate}

\item Determine a positive and a negative coterminal angle for the angle
$\frac{2\pi}{3}$.

\item Use a sketch of the unit circle to show why $\sin^2\o+\cos^2\o=1$, and
then use that formula to prove the other two forms of the pythagrean identity.

\item Write $\cos{x}$ in terms of $\tan{x}$, assuming that $x$ is in QI.

\item Consider the following sinusoidal function:
\[f(x)=-3\sin\frac{\pi}{2}(x-1)\]
\begin{enumerate}
\item What is the amplitude?
\item What is the period?
\item What is $b$ (the horizontal translation)?
\item What is $\phi$ (the phase angle)?
\item Is the phase angle leading or lagging?
\item Sketch the graph from $[0, b+\mbox{period}]$, i.e., one full period
starting from the horizontal shift point, and then extended back to 0. You must
clearly show the amplitude and the x values for each zero/min/max.
\item Looking at your sketch, what is an equivalent function in terms of
$\cos$? (Hint: try to find where a $cos$ graph overlays your graph)
\end{enumerate}
\end{enumerate}
\end{document}
