\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\newcommand{\mb}{\mathcal{B}}
\newcommand{\mr}{\mathcal{R}}
\newcommand{\vx}{\vec{x}}
\newcommand{\vy}{\vec{y}}
\newcommand{\vo}{\vec{0}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\inner}[1]{\left<#1\right>}
\begin{document}
\section*{Isometric Operators}

\begin{definition}[Isometric]
  Let $H$ be a Hilbert space and let $T\in\mb(H)$. To say that $T$ is an
  \emph{isometric} operator means $\forall\,\vx\in H$:
  \[\norm{T\vx}=\norm{\vx}\]
  An isometric operator preserves the norm.
\end{definition}

\begin{theorem}
  Let $H$ be a Hilbert space and let $T\in\mb(H)$:

  \qquad$T$ is isometric $\iff T^*T=I$
\end{theorem}

\begin{theproof}
  Assume $\vx\in H$.
  
  $\norm{T\vx}=\norm{\vx}$

  \begin{description}
  \item $\implies$ Assume $T$ is isometric.
    \begin{eqnarray*}
      \norm{T\vx}^2 &=& \norm{\vx}^2 \\
      \inner{T\vx,T\vx} &=& \inner{\vx,\vx} \\
      \inner{T^*T\vx,\vx} &=& \inner{\vx,\vx} \\
    \end{eqnarray*}
    $\therefore T^*T=I$
    
  \item $\impliedby$ Assume $T^*T=I$.
    \begin{eqnarray*}
      \norm{T\vx}^2 &=& \inner{T\vx,T\vx} \\
      &=& \inner{T^*T\vx,\vx} \\
      &=& \inner{I\vx,\vx} \\
      &=& \inner{\vx,\vx} \\
      &=& \norm{\vx}^2 \\
      \norm{T\vx} &=& \norm{\vx}
    \end{eqnarray*}
    Therefore $T$ is isometric.
  \end{description}
\end{theproof}

\begin{theorem}
  Let $H$ be a Hilbert space and let $T\in\mb(H)$ be isometric.
  $\forall\vx,\vy\in H$:
  \[\inner{T\vx,T\vy}=\inner{\vx,\vy}\]
  In other words, an isometric operator preserves the inner product.
\end{theorem}

\begin{theproof}
  Assume $\vx,\vx\in H$.
  
  $\inner{T\vx,T\vy}=\inner{T^*T\vx,\vy}=\inner{I\vx,\vy}=\inner{\vx,\vy}$
\end{theproof}

\begin{corollary}
  Let $H$ be a Hilbert space and let $T\in\mb(H)$ be isometric.
  $\forall\vx,\vy\in H$:
  \[\vx\perp\vy\iff T\vx\perp T\vy\]
\end{corollary}

\begin{theproof}
  Assume $\vx,\vy\in H$.

  $\vx\perp\vy\iff\inner{\vx,\vy}=0\iff\inner{T\vx,T\vy}=0\iff
  T\vx\perp T\vy$
\end{theproof}

\begin{theorem}
  Let $H$ be a Hilbert space and let $T\in\mb(H)$ be isometric:

  \qquad$T$ is a Hilbert space isomorphism between $H$ and $\mr(T)$.
\end{theorem}

\begin{theproof}
  $ T\vx=0\iff\norm{T\vx}=0\iff\norm{\vx}=0\iff\vx=\vo$

  Thus, the kernel is trivial and $T$ is one-to-one.

  By definition, $T$ is onto $\mr(T)$

  Therefore, $T$ is bijective.

  Also by definition: $\inner{T\vx,T\vy}=\inner{\vx,\vy}$.

  Therefore $T$ is a Hilbert space isomorphism between $H$ and $\mr(T)$.
\end{theproof}

Note that although isometric $T$ is necessarily one-to-one, it need not
be onto.

\begin{example}
  Let $H=\ell^2$ and $T(z_1,z_2,z_3,\ldots)=(0,z_1,z_2,z_3,\ldots)$.

  $T$ is isometric; however, it is not onto.
\end{example}

\end{document}
