\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Homework \#10
\end{center}

\vspace{0.5in}

\underline{Problems}

\begin{enumerate}
\item Divide $8x^4+4x^3+6x^2$ by $2x^2+1$. Show \emph{all} work and state your
  final answer in division algorithm form.

\item Consider the following graph of a polynomial:

  \begin{tikzpicture}
    \draw (-4,0) -- (4,0);
    \draw (0,-4) -- (0,4);
    \draw [domain=-2.3:2.3] plot ({\x},{0.5*(\x-2)*(\x-1)*(\x+1)*(\x+2)});
    \node [draw,circle,fill,scale=0.5] at (2,0) {};
    \node [below right] at (2,0) {$(2,0)$};
    \node [draw,circle,fill,scale=0.5] at (-1/2,45/32) {};
    \node [above left] at (-1/2,45/32) {$(-\frac{1}{2},\frac{3}{2})$};
  \end{tikzpicture}

  \begin{enumerate}
  \item What is the remainder when the polynomial is divided by $(x-2)$?
  \item What is the remainder when the polynomial is divided by
    $\left(x+\frac{1}{2}\right)$?
  \end{enumerate}

\item Consider the polynomial function:
  \[y=4x^7-4x^6-15x^5+16x^4-4x^3\]
  \begin{enumerate}
  \item Factor completely. You must show \emph{all} work (clearly), including
    selection of candidates, determining which candidates are roots, and
    successively dividing out factors. Be sure to clearly state your final
    factorized form.

  \item Sketch the graph. All intercepts must be labeled.
  \end{enumerate}

  \newpage

\item Consider the rational function:
  \[y=\frac{3(x-1)^3(x^2-9)}{(2x^3-6x^2)(x^2-4)}\]
  \begin{enumerate}
  \item What are the zeros?
  \item What are the poles?
  \item What is the y-intercept?
  \item What is the horizontal asymptote?
  \item Sketch the graph. You must label all intercepts, asymptotes, and any
    holes that may occur. All zeros must have the proper shape and the end
    behaviors must be correct.
  \end{enumerate}
\end{enumerate}

\end{document}
