\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-1003b Homework \#4
\end{center}

\vspace{0.5in}

\underline{Reading}

\bigskip

\begin{itemize}
\item Review pages 168-9 on set-builder and interval notations
\item Sections 7.7, 9.1 (on sets), 8.1, 8.2
\end{itemize}

\bigskip

\underline{Problems}

\bigskip

\begin{enumerate}
\item It costs a farmer \$0.27 to farm each square foot of land. The farmer has
  one field that is 2 hectares in size, and another that is 3 acres in size.
  How much does it cost to farm all of the land? Use the following conversions:

  1 hectare = 2.47 acres \\
  640 acres = 1 square mile \\
  1 mile = 5280 feet

\item A biker starts out from home and rides for 4 miles before getting a
  flat tire. He walks back home carrying his bike, which takes one hour
  longer than the ride. The biker can ride nine miles per hour faster than he
  can walk. How fast can he walk and how fast can he ride?

\item A parent tells his/her kids to wash the family car. Working alone, the
  first kid can wash the car 10 minutes faster than the other kid, but working
  together they can wash the car in 12 minutes. How long does it take for each
  kid to wash the car working alone?

\item Let:
  \[A=\{1,2,3,4\}\]
  \[B=\{2,4,6\}\]
  Determine the following sets:
  \begin{enumerate}
  \item $A\cup B$
  \item $A\cap B$
  \item $A-B$
  \item $A\times B$
  \end{enumerate}
\end{enumerate}
\end{document}
