\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}

\renewcommand{\d}{\delta}
\newcommand{\e}{\epsilon}

\begin{document}

\section*{Arbitrarily Close}

A new concept is needed to solve problems that algebra alone cannot solve: arbitrarily close.

\subsection*{Arbitrarily Large}

Infinity (\(\infty\)) is not an actual number, but instead is indicative of a process:

\begin{enumerate}
\item Select a positive number.
\item\label{step:large} Now select a next number that is larger than the previous number.
\item Go to \ref{step:large}.
\end{enumerate}

This is possible because the real numbers are unbounded: for every \(y\in\R\) there exists some \(x\in\R\) such
that \(x>y\).

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (-3,0) -- (3,0) node [right] {\(\infty\)};
    \node (y) [closed point] at (-1,0) {};
    \node [below] at (y) {\(y\)};
    \node (x) [closed point] at (1,0) {};
    \node [below] at (x) {\(x\)};
  \end{tikzpicture}
\end{center}

Note that as \(y\) increases, \(x\) is pushed to the right.

\begin{definition}[Arbitrarily Large]
  To say that a value \(x\in\R\) is \emph{arbitrarily large}, denoted by \(x\to\infty\), means that for every
  \(y\in\R\), \(x>y\).
\end{definition}

This also works in the negative direction.  For \(x\to-\infty\), select a negative number and then continually
select numbers that are less than the previous number.  In other words, for every \(y\in\R,x<y\).

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (3,0) -- (-3,0) node [left] {\(-\infty\)};
    \node (y) [closed point] at (1,0) {};
    \node [below] at (y) {\(y\)};
    \node (x) [closed point] at (-1,0) {};
    \node [below] at (x) {\(x\)};
  \end{tikzpicture}
\end{center}

Note that as \(y\) decreases, \(x\) is pushed to the left.

\subsection*{Arbitrarily Small}

A number can also be said to be arbitrarily small.  Like infinity, this is not an actual number, but is indicative
of a process:

\begin{enumerate}
\item Select a positive number.
\item\label{step:small} Now select a next positive number that is smaller than the previous number.
\item Go to \ref{step:small}.
\end{enumerate}

This is possible because between any two real numbers there are an infinite number of real numbers.  Thus, for any
value \(y>0\) there exists some \(x\) such that \(0<x<y\).

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (-1,0) -- (5,0);
    \node (z) [closed point] at (0,0) {};
    \node [below] at (z) {\(0\)};
    \node (y) [closed point] at (3,0) {};
    \node [below] at (y) {\(y\)};
    \node (x) [closed point] at (1.5,0) {};
    \node [below] at (x) {\(x\)};
  \end{tikzpicture}
\end{center}

Note that as \(y\) decreases, \(x\) is squeezed between \(0\) and \(y\).

\begin{definition}[Arbitrarily Small]
  To say that a value \(x\in\R^+\) is \emph{arbitrarily small}, denoted by \(x\to0^+\), means that for every
  \(y\in\R^+,0<x<y\).
\end{definition}

The Greek letters epsilon (\(\e\)) and delta (\(\d\)) are typically used to represent arbitrarily small values.

\subsection*{Distance}

The first time students are introduced to the concept of \emph{absolute value}, they are given a formula:
\[\abs{x}=\begin{cases}
x, & x\ge0 \\
-x, & x<0
\end{cases}\]
This is a perfectly good definition; however, it lacks meaning.  Instead, consider two points on the real
number line:

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (-3,0) -- (4,0);
    \node (x) [closed point] at (-1,0) {};
    \node [below] at (x) {\(-2\)};
    \node (y) [closed point] at (2,0) {};
    \node [below] at (y) {\(3\)};
  \end{tikzpicture}
\end{center}

How does one calculate the \emph{distance} from \(-2\) to \(3\)?
\[3-(-2)=5\]
How about from \(3\) to \(-2\):
\[-2-3=-5\]
But distance is an unsigned quantity (different from displacement).  Furthermore, the distance from \(-2\) to \(3\)
should be the same as the distance from \(3\) to \(-2\).  Thus, we use absolute value:
\[\abs{3-(-2)}=\abs{-2-3}=5\]

\begin{definition}[Distance]
  Let \(x,y\in\R\).  The \emph{distance} from \(x\) to \(y\) (and from \(y\) to \(x\)) is given by:
  \[d(x,y)=\abs{x-y}=\abs{y-x}\]
\end{definition}

Thus, \(\abs{x}=\abs{x-0}\), which is the distance from \(x\) to \(0\).

\subsection*{Arbitrarily Close}

\begin{definition}[Arbitrarily Close]
  To say that a value \(x\in\R\) is \emph{arbitrarily close} to another value \(c\in\R\), denoted by \(x\to c\),
  means that for all \(\e>0,\abs{x-c}<\e\).  In other words: \(c-\e<x<c+\e\).
\end{definition}

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (-4,0) -- (4,0);
    \node (c) [closed point] at (0,0) {};
    \node [below] at (c) {\(c\)};
    \node (cpe) [closed point] at (2,0) {};
    \node [below] at (cpe) {\(c+\e\)};
    \node (cme) [closed point] at (-2,0) {};
    \node [below] at (cme) {\(c-\e\)};
    \node (x) [closed point,red] at (1,0) {};
    \node [below] at (x) {\(x\)};

    \draw [<->] (-4,-2) -- (4,-2);
    \node (c) [closed point] at (0,-2) {};
    \node [below] at (c) {\(c\)};
    \node (cpe) [closed point] at (2,-2) {};
    \node [below] at (cpe) {\(c+\e\)};
    \node (cme) [closed point] at (-2,-2) {};
    \node [below] at (cme) {\(c-\e\)};
    \node (x) [closed point,red] at (-1,-2) {};
    \node [below] at (x) {\(x\)};
  \end{tikzpicture}
\end{center}

Thus, as \(\e\) gets arbitrarily small, \(x\) gets arbitrarily close to \(c\).

Also important is the negation: there exists an \(\e>0\) such that \(\abs{x-c}\ge\e\).

\bigskip

\begin{center}
  \begin{tikzpicture}
    \draw [<->] (-4,0) -- (4,0);
    \node (c) [closed point] at (0,0) {};
    \node [below] at (c) {\(c\)};
    \node (cpe) [closed point] at (2,0) {};
    \node [below] at (cpe) {\(c+\e\)};
    \node (cme) [closed point] at (-2,0) {};
    \node [below] at (cme) {\(c-\e\)};
    \node (x) [closed point,red] at (3,0) {};
    \node [below] at (x) {\(x\)};

    \draw [<->] (-4,-2) -- (4,-2);
    \node (c) [closed point] at (0,-2) {};
    \node [below] at (c) {\(c\)};
    \node (cpe) [closed point] at (2,-2) {};
    \node [below] at (cpe) {\(c+\e\)};
    \node (cme) [closed point] at (-2,-2) {};
    \node [below] at (cme) {\(c-\e\)};
    \node (x) [closed point,red] at (-3,-2) {};
    \node [below] at (x) {\(x\)};
  \end{tikzpicture}
\end{center}

\begin{theorem}
  Arbitrarily close is equivalent to equality.
\end{theorem}

\begin{proof}
  \begin{description}
    \item[]
    \item[\(\implies\)] Assume that \(x\to c\).

      ABC that \(x\ne c\).  Thus, there exist some \(d>0\) such that \(\abs{x-c}\ge d\).  So let \(\e=d\):
      \[\abs{x-c}\ge d=\e\]
      This means that there exists an \(\e>0\) such that \(\abs{x-c}\ge\e\) and hence \(x\not\to c\), contradicting
      the assumption.

      Therefore \(x=c\).

    \item[\(\impliedby\)] Assume that \(x=c\)

      Assume that \(\e>0\):
      \[\abs{x-c}=0<\e\]
      Therefore \(x\to c\).
  \end{description}
\end{proof}

\begin{example}
  Recall that one of the ways of representing a rational number is by using an infinite sequence of repeated
  decimal digits.  For example:
  \[\frac{1}{9}=0.11111\ldots=0.\overline{1}\]
  It is easy to mark \(\frac{1}{9}\) on the number line.  But how does \(0.\overline{1}\) correspond to this point?
  As each repeated digit is added, the value \(0.\overline{1}\) gets \emph{arbitrarily close} to \(\frac{1}{9}\).
  For every \(\e>0\), enough digits can eventually be added so that the result is within \(\e\) of \(\frac{1}{9}\).

  \bigskip

  \begin{center}
    \begin{tikzpicture}
      \draw [<->] (-1,0) -- (4,0);
      \node (x) [closed point] at (0,0) {};
      \node [below] at (x) {\(0\)};
      \node (y) [closed point] at (3,0) {};
      \node [below] at (y) {\(\frac{1}{9}\)};
      \node (z) at (2,0) {\((\)};
      \node [below] at (z) {\(\frac{1}{9}-\e\)};
      \node (z) [closed point,red] at (2.5,0) {};
    \end{tikzpicture}
  \end{center}

  Furthermore:
  \begin{gather*}
    \frac{1}{9}=0.\overline{1} \\
    \frac{2}{9}=0.\overline{2} \\
    \frac{3}{9}=0.\overline{3} \\
    \quad\vdots \\
    \frac{8}{9}=0.\overline{8} \\
    \frac{9}{9}=0.\overline{9}=1 \\
  \end{gather*}
  Therefore \(0.\overline{9}\) is arbitrarily close and thus equal to \(1\).
\end{example}

\begin{example}
  This works for (and is indeed a definition) for irrational numbers, which are represented by infinite sequences
  of non-repeating digits.  Consider \(\pi=3.1415926\ldots\).  Eventually, enough digits can be added in order to
  get arbitrarily closed to \(\pi\) on the number line:

  \bigskip

  \begin{center}
    \begin{tikzpicture}
      \draw [<->] (-1,0) -- (4,0);
      \node (x) [closed point] at (0,0) {};
      \node [below] at (x) {\(0\)};
      \node (y) [closed point] at (3,0) {};
      \node [below] at (y) {\(\pi\)};
      \node (z) at (2,0) {\((\)};
      \node [below] at (z) {\(\pi-\e\)};
      \node (z) [closed point,red] at (2.5,0) {};
    \end{tikzpicture}
  \end{center}
\end{example}

\end{document}
