\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}

\begin{document}

\begin{center}
  \large Math-42 Worksheet \#23

  \textbf{Discrete Probability}
\end{center}

\vspace{0.5in}

\begin{enumerate}[left=0in,itemsep=0.5in]
\item Consider rolling two fair dice.  What is the probability of:
  \begin{enumerate}
  \item Rolling a 9?
  \item Rolling a double?
  \item Rolling an even value?
  \item Rolling an even value or a 9?
  \item Rolling a double or an 8?
  \item A roll where neither die shows a 1?
  \item A roll where at least one die shows a 1?
  \end{enumerate}

\item Consider drawing 5 cards at random from a standard 52-card deck.  What is the probability of a hand containing:
  \begin{enumerate}
  \item Only one 10 of any suit?
  \item A flush (5 cards of the same suit)?
  \item A hand containing 3-of-a-kind that is neither a full house or 4-of-a-kind?
  \item A hand containing a straight-flush (5 cards in sequence in the same suit)?
  \end{enumerate}

\item A computer generates random bit strings of length 8.  What is the probability that a generated bit string
  contains:
  \begin{enumerate}
  \item Exactly five 1's.
  \item At least one 1.
  \item An even number of 1's.
  \item An even number of 1's such that neither the first nor the last position is a 1.
  \end{enumerate}

\item A horse race is run with 9 horses.  What is the probability that:
  \begin{enumerate}
  \item The 4-horse comes in first (win), second (place) or third (show)?
  \item The 4-horse and the 9-horse come in first and second in any order (an exacta)?
  \item The 4-horse, 6-horse, and the 9-horse come in first, second, and third in any order (a trifecta)?
  \end{enumerate}

\item Consider the numbers from 1 to 100.  If a number is randomly selected, what is the probability that it is:
  \begin{enumerate}
  \item The number 61?
  \item An odd number?
  \item A number that divisible by 7?
  \item A number that is divisible by 3 or 7?
  \end{enumerate}
\end{enumerate}

\end{document}
