\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{tikz}
\pagestyle{plain}
\newcommand{\m}{\mu}
\renewcommand{\o}{\sigma}
\begin{document}

\begin{center}
  \large
  Math-71 Sections 9, 11, 12

  \Large
  Practice Exam \#2
\end{center}

\vspace{0.5in}

This exam will be closed book and notes. You may use a scientific calculator; however, no other electronics are allowed.  You
may also use the instructor-provided cheatsheet.  Show all work; there is no credit for guessed answers.  Simplify your answers
unless told otherwise.  In particular, all answers should contain no negative or rational exponents.  All numerical answers
should be in exact form unless you are specifically asked for a decimal value.

\vspace{0.5in}

\begin{enumerate}[left=0pt]

\item Determine \(f'(x)\).  You do not need to simplify.
  \[f(x)=2e^{\sqrt{3x^2-1}}\]

\item Let \(f(x)=x^3-12x+5\)
  \begin{enumerate}
  \item What is the \(y\)-intercept?
  \item Find all critical points for the first derivative.
  \item Use the second derivative test to determine whether these critical points are minima, maxima, or points of
    inflection.
  \item Use the second derivative to find any points of inflection.
  \item Sketch the graph, showing and labeling all extrema, points of inflection, and the \(y\)-intercept.  You do \emph{not}
    need to determine the \(x\)-intercepts.
  \end{enumerate}

\item Let \(y=-5e^{x+2}+3\).
  \begin{enumerate}
  \item List the transformations in the proper order.
  \item What are the coordinates of the final key point?
  \item What is the equation of the final horizontal asymptote?
  \item What are the \(x\)-intercepts (if any)?
  \item What are the \(y\)-intercepts (if any)?
  \item Sketch the graph, showing and labeling the key point, horizontal asymptote, and all intercepts.
  \end{enumerate}

\item It's time for you to retire!  You have \$1,200,000 in your 401(k) that is earning about 6\% per year, compounded monthly
  on the first day of each the month.  Since you are also collecting social security, you decide that you only need to withdraw
  about \$5000 per month, which you will withdraw on the second day of each month, starting in the first month.  What is your
  account balance on the third day of the fifth month?

\item You are working quality control for a manufacturer of screws.  You are sampling a particular screw as it comes off of
  the line.  You expect the length of the screw to follow a normal distribution as follows, where the mean and standard
  deviation are expressed in centimeters (cm):
  \[p(x)=\frac{1}{0.1\sqrt{2\pi}}e^{-50(t-2)^2}\]
  \begin{enumerate}
  \item What is the mean of the screw length?
  \item What is the standard deviation of the screw length?
  \item At what \(t\) value does the corresponding bell curve have its absolute maximum?
  \item At what \(t\) values does the corresponding bell curve have its points of inflection?
  \item What is the probability that a screw length will be between 1.8 and 2.2 cm?
  \end{enumerate}

\end{enumerate}

\end{document}
