
\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Homework \#4
\end{center}

\vspace{0.5in}

\underline{Problems}

\begin{enumerate}
\item Rationalize the denominator and simplify completely. Your final answer
  should have no radicals and no negative exponents. Be careful to use absolute
  value where necessary.
  \[\frac{xyz}{\sqrt[3]{x^2y^6z^4}}\]
  
\item Consider the quadratic equation $2x^2+5x-7=0$.
  \begin{enumerate}
  \item Solve for $x$ by completing the square.
  \item Solve for $x$ using the quadratic formula.
  \end{enumerate}

\item Solve for $x$:
  \[\frac{5}{x+2}-\frac{x+5}{x-2}+\frac{28}{x^2-4}=0\]

\item Solve for $x$:
  \[4(x+1)^{\frac{1}{2}}-5(x+1)^{\frac{3}{2}}+(x+1)^{\frac{5}{2}}=0\]

\item A man stands atop a $256ft$ cliff with a  ball.
  \begin{enumerate}
  \item How long does it take for the ball to hit the ground if he simply
    releases the ball?

  \item How long does it take for the ball to hit the ground if he throws the
    ball up with a velocity of $16 ft/s$?

  \item How long does it take for the ball to hit the ground if he throws the
    ball down with a velocity of $16 ft/s$? (Hint: no additional calculations
    are
    needed).

  \item Assume that a lady is standing on the ground below the cliff and throws
    a ball up so that it passed the man on the cliff at a velocity of $16 ft/s$.
    How long would it be before the ball hits the ground? (Hint: you already
    have all the information that you need).
  \end{enumerate}
\end{enumerate}

\end{document}
