\documentclass[letterpaper, 12pt]{article}

\setlength{\topmargin}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\footskip}{0.5in}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-2in}
\addtolength{\textheight}{-\footskip}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-2in}

\pagestyle{empty}

\usepackage{amsfonts}

\begin{document}

\begin{center}
\bfseries
San Jos\'{e} State University \\
Fall 2015 \\
Math-8: College Algebra \\
Section 03: MW noon--1:15pm \\
Section 05: MW 4:30--5:45pm \\
\bigskip
Quiz \#7
\end{center}

\bigskip

Closed book and notes. No calculator allowed. All work must be shown for full
credit.

\bigskip

1. The map of a town is laid out on a grid. The police station and the fire
station are both located on Main Street, with the police station at the
position (3, -7) and the fire station at the position (-2, 5).

\bigskip

a. How far is it between the two stations?

\vspace{3in}

b. City Hall is also located on Main Street, exactly halfway between the two
stations. What is the postion of City Hall?

\newpage

2. Water boils at $212^{\circ} F$ and $100^{\circ} C$. It freezes at $32^{\circ}F$
and $0^{\circ}C$. Let $y$ be degrees Farenheit and $x$ be degrees Celsius.

\bigskip

a. Find an equation for converting from Celsius to Farenheit expressed in
slope-intercept form.

\vspace{3in}

b. Express the equation in point-slope form using the boiling point.

\vspace{2in}

c. Express the equation in general form.

\newpage

3. Consider the equation $y=\frac{8}{x^2-2}$.

\bigskip

a. Determine any x-intercept(s).

\vspace{1in}

b. Determine any y-intercept(s).

\vspace{1in}

c. Determine any discontinuities.

\vspace{1in}

d. Determine any symmetries by plugging in (-x) and/or (-y) appropriately. Be
sure to correctly name any discovered symmetry.

\vspace{2in}

e. Sketch the graph, showing all of the features found above.

\end{document}
