\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Exam \#1
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This exam is closed book and notes. You may use a calculator; however, no cell
phones or tablets are allowed. Show all work; there is no credit for guessed
answers. All values should be exact with no decimals unless you are
specifically asked for an approximate or decimal answer. Be careful to check
for extraneous solutions.

\vspace{0.5in}

\newcommand{\fillin}{\rule[-6pt]{3in}{1pt}}
\newcommand{\sfillin}{\rule[-6pt]{1in}{1pt}}

\begin{enumerate}
\item Identify each subset of the real numbers and give an example of an
  element from each set. When you give an example for a particular set, that
  example must \emph{not} be an element of any of the previous sets. So, for
  example, the example that you provide for $\Z$ must not also be in $\N$; in
  other words, it must be an element of $\Z-\N$.

  \bigskip

  \begin{tabular}{ccc}
    subset & identify & example \\
    \\
    $\N$ & \fillin & \sfillin \\
    \\
    $\Z$ & \fillin & \sfillin \\
    \\
    $\Q$ & \fillin & \sfillin \\
    \\
    $\R$ & \fillin & \sfillin
  \end{tabular}

  \vspace{1in}

\item Identify the following:

  \begin{tabular}{ll}
    $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$ & \fillin \\
    \\
    $ax^2+bx+c=0$ & \fillin
  \end{tabular}

  \newpage

\item Simplify the following. Your final answer should have no radicals and
  no negative exponents. You may assume that all variable values are positive.
  \[\left(\frac{x^7y^{-4}}{\sqrt[3]{xy^4}}\right)^{-\frac{1}{4}}\]

  \vspace{4in}

\item Rationalize the denominator:
  \[\frac{1}{\sqrt{x}-\sqrt{y}}\]

  \newpage

\item Solve by \emph{completing the square}. There is no credit for using
  the quadratic formula. Make sure that you simplify your answer.
  \[2x^2-7x-1=0\]

  \vspace{3.5in}

\item Solve for $x$ by using the least common denominator method:
  \[\frac{1}{4(x+1)^2}-\frac{1}{2(x+1)}=\frac{1}{2}\]

  \newpage

\item Solve for $x$:
  \[x^{\frac{1}{2}}+3x^{-\frac{1}{2}}=10x^{-\frac{3}{2}}\]

  \vspace{3.5in}

\item Solve for $x$:
  \[x^4+2x^2-1=0\]

  \newpage

\item Solve for $x$:
  \[3\abs{x-2}+5=10\]

  \vspace{3.5in}

\item Solve for $x$:
  \[\sqrt{2x+1}+1=x\]

\end{enumerate}

\end{document}
