\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}

\begin{document}

\begin{center}
  \large Math-42 Worksheet \#18

  \textbf{The Basics of Counting}
\end{center}

\vspace{0.5in}

\begin{enumerate}[left=0in,itemsep=0.5in]
\item Using the letters in the word: STATISTICS
  \begin{enumerate}
  \item How many ways are there to construct a sequence of two different letters?
  \item How many ways are there to construct a sequence of two different letters if the first letter must be a
    vowel and the second letter must be a consonant?
  \end{enumerate}

\item You invert in and open a sandwich show.  You offer \(3\) types of bread, \(6\) types of meat, \(5\) types of
  cheese, and \(8\) toppings (such as mustard, mayo, etc).  How many possible sandwiches are there if each sandwich
  selects one type of bread, one type of meat, one type of cheese, and one topping?

\item How many different sequences of head and tails are possible if a coin is flipped \(10\) times?

\item How many ways are there to select a man and a woman who are not married to each other from a group of \(n\)
  married couples?

\item There are \(4\) roads between town \(A\) and town \(B\), \(3\) roads between town \(B\) and town \(C\), and
  \(2\) roads between town \(A\) and town \(C\).  How many possible routes are there from town \(A\) to town \(C\),
  assuming that each road can be traversed at most one time?  (Hint: partition the routes into those that go
  through town \(B\) and those that do not.)

\item You are creating a \(6\)-letter (case-insensitive) password whose characters are limited to letters (\(26\)
  possibilities) and digits (\(10\) possibilities).  At least one character must be a digit.  How many possible
  valid passwords are there?  (Hint: consider where the first digit appears.)

\item Five committee members need to be seated at a table is facing an audience.  The committee members' names
  are: Alice, Bob, Cerida, David, and Earl.  For each of the following cases, determine the number of ways to
  seat the committee at the table (note: the cases are all separate):
  \begin{enumerate}
  \item The members can be seated in any order.
  \item Earl has to leave early, so he has requested an end chair.
  \item Alice and Cerida are best friend and want to sit next to each other.
  \item Bob and David had a big argument before the meeting and insist on sitting at opposite ends of the table.
  \end{enumerate}

\item You roll two standard six-sided dice: one red and one green.  Assuming that the dice are distinct:
  \begin{enumerate}
  \item How many possible rolls are there?
  \item How many ways are there to roll a seven?
  \item How many ways are there to roll doubles?
  \item How many ways are there to roll a seven or a double?
  \item How many ways are there to roll an even number?
  \item How many ways are there to roll an even number or a double?
  \item How many ways are there to roll an eight?
  \item How many ways are there to roll an eight or a double?
  \end{enumerate}

\item Let \(A\) be the set of positive integers less than 100 that are divisible by \(3\) and let \(B\) be the set of
  positive integers less that 100 that are divisible by \(4\).  Determine the following:
  \begin{enumerate}
  \item \(\abs{A}\)
  \item \(\abs{B}\)
  \item \(\abs{A\cap B}\)
  \item \(\abs{A\cup B}\)
  \end{enumerate}

\item You have \(5\) balls: \(3\) red, \(1\) blue, and \(1\) green.  How many distinct color arrangements are there
  if the balls are to be arranged in a row? (Hint: how many times does the same arrangement occur because of the
  red balls?)

\end{enumerate}

\end{document}
