\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{tikz}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-8 Exam Chapter 3
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This is a take-home exam. You may use your books, notes, and calculator;
however, you are not allowed to work together or get outside help. Show all
work; there is no credit for guessed answers. All values should be exact
(no decimals) unless you are specifically asked for an approximate value
answer. All domains and ranges should be expressed in interval notation.

\begin{textbf}
  Do the exam on the front side only of $8\times11$ college rule or
  graph paper. Staple all pages and make sure that your name is on the first
  page. Treat this like you would a term paper!

  Your final version is due within the first 15 minutes of class on Monday,
  December 5. Late papers or papers that do not meet the submission guidelines
  will not be accepted.
\end{textbf}

\vspace{0.5in}

\begin{enumerate}
\item Consider the following quadratic function:
  \[f(x)=-10x^2+100x-150\]
  \begin{enumerate}
  \item Put this equation in standard form by completing the square. There
    is no credit for any other method.
  \item What are the coordinates of the vertex?
  \item What is the maximum value of the function?
  \item At what value of $x$ does the maximum value occur?
  \item What are the $x$ intercepts (if any)?
  \item What are the $y$ intercepts (if any)?
  \item What is the domain?
  \item What is the range?
  \item What is the axis of symmetry?
  \item Sketch the graph. Be sure to label all key points and indicate the
    axis of symmetry.
  \end{enumerate}
\newpage
\item Consider the following polynomial function:
  \[f(x)=-x^6+x^5+8x^4-12x^3\]
  \begin{enumerate}
  \item Completely factor the polynomial function. For full credit, you must
    show how you determined your candidates, how you verified that a candidate
    was indeed a zero, and the resulting long divisions. The final
    factorization must be clearly stated.
  \item Sketch the polynomial. For full credit you must label all intercepts,
    indicate why you do or do not change sign at a zero (sign table or
    multiplicity), and show the proper shape at each zero. Simply plotting
    points or copying directly from your calculator receives zero credit.
  \item Determine (using your calculator) all minima.
  \item Determine (using you calculator) all maxima.
  \end{enumerate}
\end{enumerate}
\end{document}
