\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage[margin=1in]{geometry}
\usepackage{libertine}
\usepackage{parskip}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
\lhead{}
\chead{}
\rhead{}
\lfoot{Math-71; Sections 9,11,12; Spring 2019 --- Cavallaro}
\cfoot{}
\rfoot{Page \thepage\ of \pageref{LastPage}}
\setlength{\footskip}{0.5in}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{1pt}
\pagestyle{fancy}
\begin{document}

\begin{center}
  \emph{San Jos\'{e} State University}

  Department of Mathematics and Statistics

  {\large Spring 2019}
  
  \begin{Large}
    \bfseries
    Math-71: Calculus for Business and Aviation

    Sections 09, 11, 12
  \end{Large}
\end{center}

\vspace{0.25in}

\subsection*{Course and Contact Information}

\begin{tabular}{|p{2in}|p{4.5in}|}
  \hline
  Instructor: & Jeffery Cavallaro \\
  \hline
  Office Location: & Duncan Hall 209 (the TA room) \\
  \hline
  Telephone: & (510)-697-7231 (cell) \\
  \hline
  Email: & \url{jeffery.cavallaro@sjsu.edu} \\
  \hline
  Office Hours: & F 9am-noon (or by appointment) \\
  \hline
  Class Days/Time: & \begin{minipage}{4.5in}
    \vspace{0.1cm}
    Section 09: TR 12:00pm--1:15pm
    
    Section 11: TR 3:00pm--4:15pm
    
    Section 12: TR 4:30pm--5:45pm
    \vspace{0.1cm}
  \end{minipage} \\
  \hline
  Classroom: & Duncan Hall 318 \\
  \hline
  Prerequisites: & \begin{minipage}{4.5in}
    \vspace{0.1cm}
    Any of the following:
    \begin{itemize}
    \item A grade of C- or higher in Math 8.
    \item A grade of C or higher in Math 19.
    \item A score of 550 or higher on the math portion of the SAT.
    \item A score of 23 or higer on the math ACT.
    \item A score of 55 or higher on the CPE.
    \end{itemize}
    \vspace{0.1cm}
  \end{minipage} \\
  \hline
  Corequisite: & Math-71W (the workshop) \\
  \hline
  GE/SJSU Studies Category: & Area B4 \\
  \hline
\end{tabular}

\subsection*{Course Description}

Functions and graphs, limits, continuity, differentiation, integration, partial differentiation. Emphasis on business and
economics applications.

\subsection*{Course Learning Outcomes}

Upon successful completion of this course, students will be able to:
\begin{itemize}
\item Use the properties of exponential functions and logarithms.
\item Compute simple, compound, and continuous interest.
\item Explain the meaning of the limit of a function.
\item Compute limits.
\item Find derivatives of functions.
\item Use the concept of the derivative in applications and be able to solve problems on maxima and minima.
\item Evaluate integrals using substitutions and compute areas.
\item Compute partial derivatives.
\item Use Lagrange multipliers to find the extreme values of functions of several variables.
\item Understand probability density functions, properties of various continuous distributions including mean and
  variance.
\end{itemize}

\subsection*{Required Texts/Readings}

\subsubsection*{Corequisite}

The workshop (Math-71W) is a corequisite for this course.  Workshops are designed to help students succeed in Math courses.
In a typical workshop, students work together in small groups on problems and projects to help them better understand
concepts covered in the class.

\subsubsection*{Textbook}

\emph{College Algebra and Applied Calculus}, Larson/Hodgkins, \textbf{2th edition}, ISBN: 978-1133105060. Book and/or ebook is
fine (your preference) and we \emph{will} be using it in class.  If using a book, then the special SJSU edition in the
bookstore is suggested, since it contains chapter 16 (Probability), which we will cover.  If using the ebook then make sure
that you have a device on which you can access it during class.

\subsubsection*{Web}

We will use both canvas and webassign. All class communications, including written homework assignments and grades, are via
canvas (\url{sjsu.instructure.com}).  Webassign (\url{webassign.com}) will be used for the major portion of the
homework (see below).  Once you are registered for the course you should be able to see the course listed on your canvas
account.  Each student must purchase a webassign license (or continue to use your one year license from last semester). The
necessary webassign class code is posted in a canvas announcement and will be announced on the first day of class. Once you
register your license, you will need this class code to access the class.

\subsubsection*{Calculator}

You should have a scientific calculator for use on exams.  You may use a TI-84 during class and while doing your homework when
graphing may help you check your answers.  \emph{No other graphing calculators, cell phones, tablets, or computers are allowed
  in lieu of a scientific calculator on exams}.  In particular, use of a TI-89 is prohibited.

\subsection*{Course Requirements and Assignments}

\subsubsection*{Time}

You will need to spend a \emph{minimum} of 10 hours per week outside of class doing homework and studying. This class is
intensive and will require disciplined study habits.  Please, please, please do \emph{not} register for 16 units and commit
to a 20+ hours per week job; if you do then your chances of passing this class drop dramatically.

\subsubsection*{Reading}

Reading from the textbook will be assigned each Thursday (in class and on canvas) for the material to be
covered in the coming week.  Please read everything, not just the stuff in the boxes, prior to lecture.  Make sure that you
can work all of the example problems prior to attempting any of the homework problems.

\subsubsection*{Web Homework}

The web-based homework will be submitted via Webassign.  Due dates, which occur frequently, are listed with the assignments.
Webassign requires that you format your answers with math symbols using their answer tool.  Don't get frustrated!  It may
take a couple times for you to get the hang of it; it will get easier the more you use it.  The problems assigned on
Webassign are problems from the book; however, the software may change some of the values involved.  Since you will spend
most of your time on this homework, it constitutes the largest percentage of your grade.  So don't fall behind because there
are \emph{NO} extensions.

\subsubsection*{Written Homework}

In addition to the web-based homework, there are eleven small written homework sets.  Whereas the web-based problems are
typically based on single concepts, the written homework problem will combine concepts and will need a little more thought.
Homework will be assigned each non-exam week on Tuesday and is due on the following Tuesday by 5:45pm (when I leave campus).
Late homework will not be accepted; however, I will drop your lowest score.  See \emph{Homework Rules} for more information.

\subsubsection*{Exams}

There will be three regular exams in addition to a comprehensive final exam.  The regular exam schedule is as follows:

\bigskip

\begin{tabular}{ll}
  Exam 1 & Thursday, 2/21 \\
  Exam 2 & Thursday, 3/28 \\
  Exam 3 & Thursday, 5/9
\end{tabular}
  
\bigskip

Prior to an exam, I will post an announcement on canvas telling you exactly what to expect on the exam.  All exams are closed
book and closed notes.  A calculator (as described above) is allowed; however, any answers without supporting work receive
zero credit.  Instead of a note card, I will provide a derivative/integral cheat sheet where appropriate.

\subsubsection*{Final}

The final exam is comprehensive and is scheduled as follows:
\begin{description}
  \bfseries
\item{Section 9:} Monday, 5/20, 9:45am to 12:00pm
\item{Section 11:} Tuesday, 5/21, 2:45pm to 5:00pm
\item{Section 12:} Monday, 5/20, 2:45pm to 5:00pm
\end{description}
\emph{Do not make any travel plans that occur prior to your exam date --- attendance is mandatory.}

I like to hold a voluntary review session on dead day (5/14).

\subsection*{Determination of Grades}

Your semester grade is determined as follows:

\bigskip

\begin{minipage}{3in}
  \begin{tabular}{|c|c|}
    \hline
    Webassign Homework & 40\% \\
    \hline
    Written Homework & 10\% \\
    \hline
    Regular Exams & 30\% \\
    \hline
    Final Exam & 20\% \\
    \hline
  \end{tabular}
\end{minipage}
\begin{minipage}{3in}
  \begin{tabular}{|l|c|}
    \hline
    A+ & 100--97 \\
    A & 96--94 \\
    A- & 93--90 \\
    B+ & 89-87 \\
    B & 86-84 \\
    B- & 83-80 \\
    C+ & 79-77 \\
    C & 76-74 \\
    C- & 73-70 \\
    D+ & 69-67 \\
    D & 66-64 \\
    D- & 63-60 \\
    F & \(<\)60 \\
    \hline
  \end{tabular}
\end{minipage}

A grade of C- or higher fulfills the Area B4 GE requirement.

\subsection*{Course Content}

We will cover materials from chapters 7--11, 13, and 16 as follows:

\begin{tabular}{|l|l|c|}
  \hline
  \textbf{Sections} & \textbf{Weeks} \\
  \hline
  7.1--7.7 & 3 \\
  \hline
  8.4--8.6 & 1.5 \\
  \hline
  9.1--9.2 & 1 \\
  \hline
  10.1--10.5 & 2 \\
  \hline
  11.1--11.4 & 2.5 \\
  \hline
  16.3--16.4 & 1 \\
  \hline
  13.1--13.4 & 2.5 \\
  \hline
\end{tabular}

There will also be review material from chapters 0, 1, 4, and 5.  Students will be responsible for self-review of this
material; however, I will do some light review in class when needed.  The workshop and office hours are also good places to
obtain help with this review material.

\subsection*{Classroom Protocol}
  
\subsubsection*{Attendance}

I will not take attendance after the first week; however, it is important that you come (on time) to every class. The book
has more information than we could possibly cover, so I will highlight in class what is important. Bring your book and
calculator to every class meeting. If you miss a class, it is your responsibility to talk to your peers and find out what you
missed.

\subsubsection*{Holidays}

Class will not meet during Spring break (4/2 and 4/4).

\subsection*{University Policies}

Per University Policy S16-9 (\url{http://www.sjsu.edu/senate/docs/S16-9.pdf}), information relevant to all courses:
academic integrity, accommodations, dropping and adding, consent for recording of class, etc., is available on the Office of
Graduate and Undergraduate Programs’ Syllabus Information web page at \url{http://www.sjsu.edu/gup/syllabusinfo}.
Please make sure to review these university policies and resources.

\end{document}
