\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\newcommand{\F}{\mathbb{F}}
\newcommand{\vx}{\vec{x}}
\newcommand{\vy}{\vec{y}}
\newcommand{\vu}{\vec{u}}
\newcommand{\vw}{\vec{w}}
\newcommand{\vz}{\vec{0}}
\newcommand{\vzp}{\vec{0'}}
\begin{document}
\section*{Subspaces}
  
\begin{definition}[Subspace]
  Let $V$ be a vector space over a field $\F$ and let $S\subseteq V$. To say
  that $S$ is a \emph{subspace} of $V$ means that $S$ is also a vector space
  over the same field $\F$ using the same operations of vector addition and
  scalar multiplication as $V$.

  $\{\vz\}$ is called the \emph{zero subspace} and is a subspace of all
  vector spaces.
  
  The zero subspace and $V$ are called the \emph{trivial} subspaces of $V$. All
  other subspaces of $V$ are called \emph{non-trivial}.

  To say that $S$ is a \emph{proper} subspace of $V$ means that $S$ is a
  subspace of $V$ but $S\ne V$.
\end{definition}

\begin{theorem}[Subspace Test]
  Let $V$ be a vector space over a field $\F$.

  $S\subseteq V$ is a subspace of $V$ iff:
  \begin{enumerate}
  \item $\vz\in S$
  \item $S$ is closed under vector addition.
  \item $S$ is closed under scalar multiplication.
  \end{enumerate}
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item $\implies$ Assume $S$ is a subspace of $V$

    By definition, the closure properties hold and there exists additive
    identity $\vzp\in S$ \\
    Assume $\vx\in S$ \\
    $\vx+\vzp=\vx$ \\
    But $\vx\in V$ as well, so $\vx+\vz=\vx$ \\
    $\vx+\vzp=\vx+\vz$ \\
    Thus, $\vzp=\vz$, and so $\vz\in S$

    Therefore, the three properties hold.

  \item $\impliedby$ Assume the three properties hold

    Note that $S$ inherits all of the vector space axioms from $V$ with the
    exceptions of closure, additive identity, and additive inverses. Closure and
    identity are supplied by the assumed properties.

    For inverses, assume $x\in S$ \\
    By closure, $(-1)x=(-x)\in S$

    Therefore, all ten axioms hold, and $S$ is a subspace of $V$.
  \end{description}
\end{theproof}

\newpage

\begin{example}
  \listbreak
  \begin{enumerate}
  \item Let $\F_n[x]$ denote all polynomials of degree $\le n$ using scalars
    and coefficients from $\F$. This is a subspace of $\F[x]$.

  \item Let $C(\R)$ denote all continuous functions $f:\R\to\R$. This is a
    subspace of $\mathcal{F}(\R,\R)$.
  \end{enumerate}

  But note that polynomials of degree exactly $n$ is not a subspace since it
  does not include the zero polynomial and closure fails. For example:
  $(x^3+x^2)$ and $(-x^3+x^2)$ are both degree 3 polynomials; however:
  \[(x^3+x^2)+(-x^3+x^2)=2x^2\]
  which is only degree 2.
\end{example}

\begin{theorem}
  Let $V$ be a vector space over a field $\F$ and let $\{S_i\mid i\in I\}$ be a
  family of subspaces of $V$:
  \[S=\bigcap_{i\in I}S_i\]
  is a subspace of $V$.
\end{theorem}

\begin{theproof}
  Assume $i\in I$

  $S_i$ is a subspace of $V$, so $\vz\in S_i$

  $\therefore \vz\in S$

  Assume $\vx,\vy\in S$ \\
  $\vx,\vy\in S_i$ \\
  So by closure, $\vx+\vy\in S_i$ \\
  Thus $\vx+\vy\in S$

  Therefore $S$ is closed under vector addition.

  Assume $c\in\F$ \\
  By closure, $c\vx\in S_i$ \\
  Thus $c\vx\in S$

  Therefore $S$ is closed under scalar multiplication.

  Therefore, by the subspace test, $S$ is a subspace of $V$.
\end{theproof}

\begin{theorem}
  Let $V$ be a vector space and let $U$ and $W$ be two subspaces of $V$:
  \[U+W=\{\vu+\vw\mid\vu\in U\ \mbox{and}\ \vw\in W\}\]
  is a subspace of $V$.
\end{theorem}

\begin{theproof}
  Since $U$ and $W$ are subspaces of $V$, $\vz\in U$ and $\vz\in W$

  Therefore, $\vz=\vz+\vz\in U+W$

  Assume $\vx,\vy\in U+V$ \\
  There exists $\vu_x\in U$ and $\vw_x\in W$ such that $\vx=\vu_x+\vw_x$ \\
  Also, there exists $\vu_y\in U$ and $\vw_y\in W$ such that
  $\vy=\vu_y+\vw_y$ \\
  $\vx+\vy=(\vu_x+\vw_x)+(\vu_y+\vw_y)=(\vu_x+\vu_y)+(\vw_x+\vw_y)$ \\
  But by closure $\vu_x+\vu_y\in U$ and $\vw_x+\vw_y\in W$ \\
  Thus, $\vx+\vy\in U+W$

  Therefore $U+W$ is closed under vector addition.

  Assume $c\in\F$ \\
  $c\vx=c(\vu_x+\vw_x)=c\vu_x+c\vw_x$ \\
  But by closure, $c\vu_x\in U$ and $c\vw_x\in W$ \\
  Thus, $c\vx\in U+W$

  Therefore $U+W$ is closed under scalar multiplication.

  Therefore, by the subspace test, $U+W$ is a subspace of $V$.
\end{theproof}

\end{document}
