\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{tikz}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-8 Exam \#1
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This exam is closed book and notes. You may use a calculator; however, no other
electronics are allowed. Show all work; there is no credit for guessed
answers. All answers should be in exact values, unless you are specifically
asked for an approximate value.

\vspace{0.5in}

Helpful Stuff:
\[d=rt\]
\[\frac{1}{t_1}+\frac{1}{t_2}=\frac{1}{t}\]
\[h=h_0+v_0t-16t^2\]
\[x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}\]
\newpage
\begin{enumerate}
\item A family is going on a fishing trip to a cabin near a lake. They have a
  lot of stuff, so they are going to take two cars. The cars leave at the same
  time, take the same route, and drive at a fairly constant speed. The first
  car goes 70 mph and arrives one hour before the second car, which is only
  going 60 mph. What is the duration of each car's trip?
\newpage
\item A parent tells his/her kids to wash the family car. Working alone, the
  first kid can wash the car 10 minutes faster than the other kid, but working
  together they can wash the car in 12 minutes. How long does it take for each
  kid to wash the car working alone?
\newpage
\item A man stands on a 640 foot cliff.
  \begin{enumerate}
  \item He throws a rock \emph{up} into the air with an initial velocity of 16
    ft/s. How long does it take for the rock to fall halfway down the cliff?
    Use the complete-the-square method to solve - do \emph{not} use the
    quadratic formula (Hint: keep the negative answer).
    \vspace{5in}
  \item Without doing any additional calculations, how long does it take for
    the rock to fall halfway down the cliff if the man throws the rock
    \emph{down} at 16 ft/s.
  \end{enumerate}
\newpage
\item Solve for $x$, stating the answer using interval notation (Hint: you
  should be able to state the answer to part (b) without any extra work).
  \begin{enumerate}
  \item $\abs{2-3x}<1$
    \vspace{5in}
  \item $\abs{2-3x}\ge1$
  \end{enumerate}
\newpage
\item Solve for $x$, stating the answer using interval notation.
  \[\frac{x^3+x^2-2x}{x^2-5x+6}<0\]
\end{enumerate}

\end{document}
