\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{tikz}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Exam \#2
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This exam is closed book and notes. You may use a calculator; however, no cell
phones or tablets are allowed. Show all work; there is no credit for guessed
answers. All values should be exact unless you are specifically asked for an
approximate value answer. In particular, trig answers should be left in terms
of $\pi$ unless otherwise directed.

\vspace{0.5in}

\begin{enumerate}
\item Consider the following polynomial function:
\[f(x)=x^6-8x^5+17x^4+6x^3-44x^2+8x+32\]
\begin{enumerate}
\item Completely factor it into linear factors. It must be \emph{clear} how
you obtained candidate factors, determined that they are indeed factors, and
how you reduced the problem for each found factor (i.e., long or synthetic
division).
\newpage
\item What is the end behavior as $x\to\infty$?
\vspace{1in}
\item What is the end behavior as $x\to-\infty$?
\vspace{1in}
\item What are the x-intercepts (if any)?
\vspace{1in}
\item What are the y-intercepts (if any)?
\vspace{1in}
\item Sketch a graph of the function. You must show and label all zeros and
intercepts and show the proper behavior and shape at each zero.  Your sketch
need not be to scale.
\end{enumerate}
\newpage
\item Consider the following rational function:
\[f(x)=\frac{x^2+3x-4}{x^3-x^2-6x}\]
\begin{enumerate}
\item What are the zeros (if any)?
\vspace{0.5in}
\item What are the vertical asymptotes (if any)?
\vspace{0.5in}
\item What are the horizontal asymptotes (if any)?
\vspace{0.5in}
\item What is the end behavior for $x\to+\infty$? If it is asymptotic, be
sure to indicate whether the asymptote is approached from below or above and
why.
\vspace{0.5in}
\item What is the end behavior for $x\to-\infty$? If it is asymptotic, be
sure to indicate whether the asymptote is approached from below or above and
why.
\vspace{0.5in}
\item What are the y-intercepts (if any)?
\vspace{0.5in}
\item Sketch a graph of the function. You must show and label all zeros,
asymptotes, and intercepts, with the correct behavior at each.  Your sketch
need not be to scale.
\end{enumerate}
\newpage
\item Some archaeologists are digging at what appears to be a pre-Columbian
human campsite in California.  They find some animal bones with human teeth
marks on them.  Upon carbon-14 analysis, it is found that the bones have 75\%
of their original $C_{14}$.  About how old are the bones, and hence the
campsite?  The half-life of $C_{14}$ is 5730 years.
\vspace{2in}
\item Consider the following triangle:

\begin{tikzpicture}[scale=0.5]
\draw (0,0) -- (12,0) -- (12,5) -- (0,0);
\draw (11.5,0) -- (11.5,0.5) -- (12,0.5);
\node at (2.5,0.5) {$\theta$};
\node [below] at (6,0) {12};
\node [right] at (12,2.5) {5};
\end{tikzpicture}

Determine all six basic trigonometric ratios.
\newpage
\item You want to measure the height of a tree; however, you can't reach the
top to measure it with a tape measurer. So you stand 10 feet from the tree,
look up to the top of the tree at an angle of $45^{\circ}$ and look down at the
bottom of the tree at an angle of $\frac{\pi}{6}$ radians.  How tall is the
tree (to the nearest tenth of a foot)?

\end{enumerate}

\end{document}
