\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{siunitx}
\usepackage{tikz}
\pagestyle{plain}
\begin{document}

\begin{center}
  \large
  Math-71 Sections 9, 11, 12

  \Large
  Final Exam
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This exam is closed book and notes. You may use a scientific calculator; however, no other electronics are allowed.  You may
also use the instructor-provided cheatsheet.  Show all work; there is no credit for guessed answers.  Simplify your answers
unless told otherwise.  In particular, all answers should contain no negative or rational exponents.  All numerical answers
should be in exact form unless you are specifically asked for a decimal value.  

\vspace{0.5in}

\begin{enumerate}[left=0pt]
\item Consider the function:
  \[f(x)=\frac{x-2}{x^2+3x-10}\]
  \begin{enumerate}
  \item Determine \(\displaystyle\lim_{x\to2}f(x)\) if it exists.  Otherwise, state \emph{DNE}.

    \vspace{2.5in}

  \item Using interval notation, describe where \(f(x)\) is continuous.
  \end{enumerate}

  \newpage

\item Determine \(f'(x)\) for \(f(x)=3x^4\).

  \vspace{1in}

\item Determine \(f'(x)\) for \(\displaystyle f(x)=\frac{x}{\pi}\).

  \vspace{1in}

\item Determine \(f'(x)\) for \(\displaystyle f(x)=\frac{e^2}{x}\).

  \vspace{1in}

\item Determine \(f'(x)\) for \(\displaystyle f(x)=\frac{3e^{x^2}}{2}\).

  \vspace{1in}

\item Determine \(f'(x)\) for \(f(x)=\ln(x^2+2)\)

  \vspace{1in}

\item Determine \(f'(x)\) for \(f(x)=2x^3-3x^2+50x-100\)

  \newpage

\item Using the product and chain rules, determine \(f'(x)\) for \(f(x)=\ln(x)\sqrt{x^2+1}\)

  \vspace{4in}

\item Using the quotient and chain rules, determine \(f'(x)\) for \(f(x)=\frac{e^x}{x^3-2}\)

  \newpage

\item Determine \(\displaystyle\int3x^4dx\).

  \vspace{1.5in}

\item Determine \(\displaystyle\int\frac{x}{\pi}dx\).

  \vspace{1.5in}

\item Determine \(\displaystyle\int\frac{e^2}{x}dx\).

  \vspace{1.5in}

\item Determine \(\displaystyle\int_0^1(2x^3-3x^2+50x-100)dx\)

  \newpage

\item Determine \(\displaystyle\int{2xe^{x^2}}dx\).

  \vspace{4in}

\item Determine \(\displaystyle\int\frac{2x}{x^2+1}dx\).

  \newpage

\item You get your first paycheck from a new job.  On March 1, you go to the bank and open a savings account that pays interest
  of 3\% annually, compounded monthly, with an initial deposit of \$1000.  You set up an auto-deposit from your paycheck that
  will deposit \$500 each month on the first of the month to the account, starting in April.  In May, you need to withdraw
  \$750 from your account to pay some bills.  What is your account balance on June 2?

  \newpage

\item After watching a famous episode of the Nickelodean TV show iCarly, you decide to start your own penny tee t-shirt
  business.  You decide that a good monthly demand function (with respect to selling price, in dollars) is given by:
  \[n(p)=2000-100p\]
  You expect monthly fixed costs to be \$1000 and variable costs to be \$1 per shirt.
  \begin{enumerate}
  \item Determine the monthly revenue function \(R(p)\).

    \vspace{0.75in}

  \item Determine the monthly cost function \(C(p)\).

    \vspace{1in}

  \item Determine the monthly profit function \(P(p)\).

    \vspace{1.25in}

  \item At what per-shirt sales price is profit maximized?

    \vspace{2in}

  \item Prove (either by test points or concavity) that your answer is in fact a maximum.
  \end{enumerate}

  \newpage

\item You are working quality control at a precision ball-bearing factory.  The radius of each ball-bearing as it comes off of
  the production line follows a normal distribution as follows:
  \[p(x)=\frac{1}{0.01\sqrt{2\pi}}e^{\frac{-(x-2)^2}{0.0002}}\]
  where the radius \(x\) is measured in millimeters.
  \begin{enumerate}
  \item What is the mean radius of the ball-bearings?

    \vspace{1in}

  \item What is the standard deviation of the radius of the ball-bearings?

    \vspace{1in}

  \item At what \(x\) value does the corresponding bell curve have its absolute maximum?

    \vspace{1in}

  \item At what \(x\) values does the corresponding bell curve have its points of inflection?

    \vspace{1in}

  \item What is the probability that a ball-bearing radius is between \SI{1.97}{mm} and \SI{2.03}{mm}?
  \end{enumerate}

  \newpage

\item A new eBike company called Telfon, run by entrepreneur and international playboy Allen Tusk, is going to build
  its bikes at two factories: one in Singapore and one in South Korea.  Let \(x\) be the number of bikes made in the
  Singapore plant and \(y\) be the number of bikes made in the South Korea plant.  The cost function for making the bikes is
  given by:
  \[C(x,y)=\frac{1}{2}x^2+4x+\frac{1}{4}y^2+8y\]
  The initial combined order will be for 10,000 bikes.  Using the Lagrange multiplier method, determine how these 10,000 bikes
  should be split between the two factories in order to minimize cost.

  \newpage

\item You work in the advertising department for a new fast-food restaurant that is launching in the bay area.  You decide to
  run a major``branding'' advertising campaign with a new radio spot (commercial).  The goal is for people to both hear the
  commercial and remember the company name and business when asked - thus establishing your brand in their mind.  This makes it
  more likely that people will try your restaurant when they are hungry.  Your advertising agency estimates that the rate of
  change of people successfully branded is given by:
  \[\frac{dx}{dt}=xe^{-x^2}\]
  where \(x\) is millions of people branded and \(t\) is the number of months that the planned advertising campaign is running.
  How many potential customers are branded after 2 months?
\end{enumerate}

\end{document}
