\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-08 Homework \#10
\end{center}

\vspace{0.5in}

\underline{Reading}

\begin{itemize}
\item Text book section 2.1 to 2.3
\end{itemize}

\underline{Problems}

\begin{enumerate}
\item The corners of a square are given by the following coordinates:
  \[(-1,-1), (-4,5), (2,8), (5,2)\]
  \begin{enumerate}
  \item Determine the equation of the circle inscribed inside the square.
  \item Determine the equation of the line parallel to the side from
    $(-1,-1)$ to $(5,2)$ and through the center of the circle.
  \item Determine the equation of the line perpendicular to the side from
    $(-1,-1)$ to $(5,2)$ and through the center of the circle.
  \end{enumerate}

\item Consider the line through the points (1,5) and (1,-1).
  \begin{enumerate}
  \item Determine the equation of the line.
  \item Determine the equation of the line parallel to the first line and
    through the point (-2,-2).
  \item Determine the equation of the line perpendicular to the first line
    and through the point (-2,-2).
  \end{enumerate}

\item An object moving in a straight line at constant velocity has its
  equation of motion given by: $s=s_0+v_0t$, where $s$ is the position at time
  $t$, $s_0$ is the initial position, and $v_0$ is the constant speed.
  \begin{enumerate}
    \item What are the slope and y-intercept for this linear model?
    \item An object is moving at 10 ft/s. At time 5 seconds the object is
      at position $s=60$ feet. What is the initial position $s_0$?
  \end{enumerate}

\item A manufacturing firm buys a new machine for \$150,000. After the machine
  is fully depreciated, it will have a salvage value of \$5,000. Assuming a
  15-year straight-line depreciation model, what will be the value of the
  machine after 10 years?
\end{enumerate}
\end{document}
