\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}

\begin{document}

\begin{center}
  \large Math-42 Worksheet \#20

  \textbf{Permutations and Combinations}
\end{center}

\vspace{0.5in}

\begin{enumerate}[left=0in,itemsep=0.5in]
\item How many bit strings of length \(10\) contain:
  \begin{enumerate}
  \item Exactly three \(1\)'s.
  \item At most three \(1\)'s.
  \item At least three \(1\)'s. (Hint: not zero, one, or two \(1\)'s.)
  \item An equal number of \(0\)'s and \(1\)'s.
  \end{enumerate}

\item There are nine horses running in a horse race.  How many ways are there for the horses to come in
  first (win), second (place), and third (show) when:
  \begin{enumerate}
  \item There are no restrictions.
  \item The number \(8\) horse is scratched from the race (i.e., drops out).
  \item The number \(4\) horse comes in second.
  \item The number \(3\) horse comes in first and the number \(9\) horse comes in third.
  \item The number \(3\) horse comes in first and the number \(9\) horse comes in fifth.
  \end{enumerate}
  
\item How many distinct ways are there to arrange the letters in the word SUCCESS:
  \begin{enumerate}
  \item With no restrictions.
  \item When the two C's must be together.
  \item When the two C's must be together and the three S's must be together.
  \item When the E can only follow a C.
  \end{enumerate}

\item A standard deck has \(52\) cards: \(4\) suits (clubs, diamonds, hearts, spades) and \(13\) ranks per suit
  (\(2\)--Ace).  A poker hand is any \(5\) of the \(52\) cards.
  \begin{enumerate}
  \item How many possible poker hands are there?
  \item A three-of-a-kind hand consists of \(3\) cards of the same rank and two additional cards whose ranks do not
    match the three nor do they match each other (e.g.: AC,AD,AH,2D,5C).  How many possible three-of-a-kind hands
    are there?
  \item A full house is like a three-of-a-kind; however, the two additional cards have the same rank as each other
    (e.g.: AC,AD,AH,10D,10S).  How many full house hands are there?
  \item How many four-of-a-kind hands are there?
  \end{enumerate}

\item A committee of \(4\) people must be selected from a group consisting of \(6\) men and \(4\) women.  How many
  possible committees can be formed if:
  \begin{enumerate}
  \item There are no restrictions.
  \item The committee must include at least one woman.
  \item The committee must include at least two woman.
  \item Bob and Nancy demand to serve together or not at all.
  \item Ed and Jose refuse to serve together.
  \end{enumerate}
\end{enumerate}

\end{document}
