\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\begin{document}
\section*{One-sided Axioms}

The traditional definition of a group uses a two-sided identity and two-sided
inverses. It is possible to give a weaker definition of a group using a
one-sided identity and matching one-sided inverses:

\begin{theorem}
  Let $G$ be a semigroup. $G$ is a group iff the following two properties hold:
  \begin{enumerate}
  \item $G$ contains a left identity element:
    \[\exists\,e\in G,\forall\,a\in G,ea=a\]
  \item Each element in $G$ contains a left inverse element that is also in
    $G$:
    \[\forall\,a\in G,\exists\,a^{-1}\in G,a^{-1}a=e\]
  \end{enumerate}
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item $\implies$ Assume $G$ is a group.

    $G$ has a two-sided identity $e$, which is also one-sided. \\
    $\forall\,a\in G$, $a$ has a two-sided inverse, which is also one-sided. \\
    $\therefore$ the two properties hold.

  \item $\impliedby$ Assume that $G$ has a left-sided identity and
    left-sided inverses.
    
    Assume $a\in G$:
    \begin{eqnarray*}
      ee &=& e \\
      (a^{-1}a)e &=& a^{-1}a \\
      (a^{-1})^{-1}((a^{-1}a)e) &=& (a^{-1})^{-1}(a^{-1}a) \\
      ((a^{-1})^{-1}a^{-1})(ae) &=& ((a^{-1})^{-1}a^{-1})a \\
      e(ae) &=& ea \\
      ae &=& a \\
    \end{eqnarray*}
    $\therefore e$ is a right identity as well.
    \begin{eqnarray*}
      a^{-1}a &=& e \\
      (a^{-1}a)a^{-1} &=& ea^{-1} \\
      (a^{-1}a)a^{-1} &=& a^{-1} \\
      (a^{-1})^{-1}((a^{-1}a)a^{-1}) &=& (a^{-1})^{-1}a^{-1} \\
      ((a^{-1})^{-1}a^{-1})(aa^{-1}) &=& e \\
      e(aa^{-1}) &=& e \\
      aa^{-1} &=& e \\
    \end{eqnarray*}
    $\therefore a^{-1}$ is a right inverse as well.
    
    $G$ is associative, has a two-sided identity, and has two-sided inverses. \\
    $\therefore G$ is a group.
  \end{description}
\end{theproof}

A similar theorem exists for a right identity and right inverses as well, but
not for a mix of a left and a right.

\begin{theorem}
  Let $G$ be a semigroup. $G$ is a group iff the following two properties hold:
  \begin{enumerate}
    \item $\forall\,a,b\in G,ax=b$ has a solution in $G$.
    \item $\forall\,a,b\in G,xa=b$ has a solution in $G$.
  \end{enumerate}
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item $\implies$ Assume $G$ is a group.

    Previously proven.

  \item $\impliedby$ Assume $\forall\,a,b\in G,ax=b$ and $xa=b$ have solutions
    in $G$.

    Assume $a,b\in G$
    
    Let $e\in G$ be a solution for $xa=a$ \\
    $ea=a$ \\
    Let $c$ be a solution for $ax=b$ \\
    $ac=b$ \\
    $eb=e(ac)=(ea)c=ac=b$ \\
    $\therefore e$ is a left identity for $G$.

    Let $a^{-1}\in G$ be a solution for $xa=e$ \\
    $a^{-1}a=e$ \\
    $a^{-1}$ is a left inverse for $a$ \\
    $\therefore G$ has left inverses.

    $\therefore$, by the one-sided test, $G$ is a group.
  \end{description}
\end{theproof}

\end{document}
