\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\newcommand{\vx}{\vec{x}}
\newcommand{\vy}{\vec{y}}
\newcommand{\vo}{\vec{0}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\renewcommand{\d}{\delta}
\newcommand{\e}{\epsilon}
\begin{document}
\section*{Continuity}

\begin{definition}[Continuous]
  Let $T:E_1\to E_2$ be a mapping of normed spaces. To say that $T$ is
  continuous at $\vx$ means $\forall\,(\vx_n)$ in $E_1$:
  \[\vx_n\to\vx\implies T(\vx_n)\to T(\vx)\]
  To say that $T$ is continuous means $T$ is continuous at
  $\forall\,\vx\in E_1$.
\end{definition}

\begin{theorem}
  Let $E$ be a normed space. $\norm{\cdot}:E\to\R$ is continuous.
\end{theorem}

\begin{theproof}
  Assume $\vx\in E$. \\
  Assume $(\vx_n)$ is a sequence in $E$ such that $\vx_n\to\vx$.
  \[\abs{\norm{\vx_n}-\norm{\vx}}\le\norm{\vx_n-\vx}\to0\]
  Therefore $\norm{\cdot}$ is continuous.
\end{theproof}

\begin{theorem}
  Let $L:E_1\to E_2$ be a mapping of normed spaces and let $U\subseteq E_2$.
  TFAE:
  \begin{enumerate}
  \item $L$ is continuous.
  \item $U$ open $\implies$ $L^{-1}[U]$ open.
  \item $U$ closed $\implies$ $L^{-1}[U]$ closed.
  \end{enumerate}
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item $1\to2$: Assume $L$ is continuous.

    Assume $U$ is open. \\
    Assume $\vx\in L^{-1}[U]$. \\
    Since $U$ is open, $\exists\,\e>0,B(L\vx,\e)\subset U$. \\
    But since $L$ is continuous, $\exists\,\d>0$ such that
    $\forall\,\vx_n\in E$:
    \[\norm{\vx_n-\vx}<\d\implies\norm{L\vx_n-L\vx}<\e\]
    But $L\vx_n\in U$, so $\vx_n\in L^{-1}[U]$. \\
    Therefore $B(\vx,\d)\in L^{-1}[U]$ and thus $L^{-1}[U]$ is open.

  \item $2\to1$: Assume $U$ open $\implies$ $L^{-1}[U]$ open.

    Assume $\vx\in E_1$. \\
    And so $L\vx\in E_2$. \\
    Assume $\e>0$. \\
    Consider the open ball $U=B(L\vx,\e)$. \\
    By assumption, $L^{-1}[U]$ is also open. \\
    But $\vx\in L^{-1}[U]$, so $\exists\,\d>0$ such that
    $B(\vx,\d)\subset L^{-1}[U]$. \\
    Assume $\vx_n\in E_1$ such that $\norm{\vx_n-\vx}<\d$. \\
    This means that $\vx_n\in B(\vx,\d)$, and hence in $L^{-1}[U]$. \\
    Thus, $L\vx_n\in U$ and $\norm{L\vx_n-L\vx}<e$.

    Therefore, $L$ is continuous.

  \item $2\implies3$: Assume $U$ open $\implies$ $L^{-1}[U]$ open.

    Assume $U$ is closed. \\
    Thus $E_2\setminus U$ is open. \\
    Note that $L^{-1}[U]\cap L^{-1}[E_2\setminus U]=\emptyset$, otherwise $L$ is
    not well-defined. \\
    By assumption, $L^{-1}[E_2\setminus U]=E_1\setminus L^{-1}[U]$ is open.

    Therefore $L^{-1}[U]$ is closed.

  \item $3\implies2$: Assume $U$ closed $\implies$ $L^{-1}[U]$ closed.
    
    Assume $U$ is open. \\
    Thus $E_2\setminus U$ is closed. \\
    Note that $L^{-1}[U]\cap L^{-1}[E_2\setminus U]=\emptyset$, otherwise $L$ is
    not well-defined. \\
    By assumption, $L^{-1}[E_2\setminus U]=E_1\setminus L^{-1}[U]$ is closed.

    Therefore $L^{-1}[U]$ is open.
  \end{description}
\end{theproof}

\begin{theorem}
  Let $L:E_1\to E_2$ be a linear map of normed spaces:

  \qquad$L$ is continuous (everywhere in $E_1$) iff it is continuous at some
  $\vx_0\in E_1$
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item Assume $L$ is continuous everywhere in $E_1$.

    Therefore it must be continuous at some $\vx_0\in E_1$.

  \item Assume $L$ is continuous at some $\vx_0\in E_1$.

    Assume $\vx\in E_1$. \\
    Assume $(\vx_n)$ is a sequence in $E_1$ such that $\vx_n\to\vx$. \\
    Thus, the sequence $(\vx_n-\vx+\vx_o)$ converges to $\vx_0$. \\
    $\norm{L\vx_n-L\vx}=\norm{L\vx_n-L\vx+L\vx_0-L\vx_0}=
    \norm{L(\vx_n-\vx+\vx_0)-L\vx_0}\to0$

    Therefore, $L$ is continuous at $\vx$, and thus is continuous everywhere
    in $E_1$.
  \end{description}
\end{theproof}

\newpage

\begin{theorem}
  Let $L:E_1\to E_2$ be a linear map of normed spaces.

  \qquad$L$ is continuous iff $L$ is bounded.
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item $\implies$ Assume $L$ is continuous.

    ABC: $L$ is not bounded. \\
    $\forall\,M>0,\exists\,\vx\in E_1,\norm{L\vx}>M\norm{\vx}$ \\
    Let $M=n$. \\
    So $\norm{L\vx}>n\norm{\vx}$ for some $\vx\in E_1$. \\
    Thus, $\norm{L\frac{\vx}{n\norm{\vx}}}>1$. \\
    Let $y_n=\frac{\vx}{n\norm{\vx}}$. \\
    $\norm{y_n}=\norm{\frac{\vx}{n\norm{\vx}}}=
    \frac{1}{n}\norm{\frac{\vx}{\norm{\vx}}}=\frac{1}{n}\cdot1=
    \frac{1}{n}\to0$. \\
    But $\norm{L\vy_n}>1\ne0$. \\
    Therefore $L$ is not continuous. \\
    CONTRADICTION!

    Therefore, $L$ is bounded.

  \item $\impliedby$ Assume $L$ is bounded.

    Assume $(\vx_n)$ is a sequence in $E_1$ such that $\vx_n\to\vo$. \\
    $\norm{L\vx_n-L\vo}=\norm{L\vx_n-\vo}=\norm{L\vx_n}\le
    \norm{L}\norm{\vx_n}\to0$

    Therefore $L$ is continuous at $\vo\in E_1$ and thus is continuous
    everywhere in $E_1$.
  \end{description}
\end{theproof}

\end{document}
