\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\begin{document}
\section*{Integral Domains}

\begin{definition}
  To say that a $R$ is an \emph{integral domain} means:
  \begin{enumerate}
  \item $R$ is a commutative ring with unity $1\ne0$
  \item $R$ has no zero divisors
  \end{enumerate}
\end{definition}

\begin{theorem}
  Let $R_1$ and $R_2$ be rings. $R_1\times R_2$ is never an integral domain.
\end{theorem}

\begin{theproof}
  Let $r_1\in R_1,r_1\ne0$ \\
  Let $r_2\in R_2,r_2\ne0$ \\
  $(r_1,0)\in R_1\times R_2$ \\
  $(0,r_2)\in R_1\times R_2$ \\
  $(r_1,0)(0,r_2)=(0,0)$ \\
  $(r_1,0)$ and $(0,r_2)$ are zero divisors in $R_1\times R_2$ \\
  $\therefore R_1\times R_2$ is not an integral domain.
\end{theproof}

\begin{theorem}
  $F$ is a field $\implies F$ is an integral domain.
\end{theorem}

\begin{theproof}
  Assume $F$ is a field \\
  $F$ is a commutative ring with unity $1\ne0$ \\
  Assume $a\in F,a\ne0$ \\
  Assume $b\in F,ab=0$ \\
  $a^{-1}\in F$ \\
  $a^{-1}(ab)=a^{-1}0$ \\
  $(a^{-1}a)b=0$ \\
  $1b=0$ \\
  $b=0$ \\
  Thus, $a$ is not a zero divisor of $F$ \\
  $F$ has no zero divisors \\
  $\therefore F$ is an integral domain.
\end{theproof}

\begin{theorem}
  $F$ is a finite integral domain $\implies F$ is a field.
\end{theorem}
\newpage
\begin{theproof}
  Assume $F$ is a finite integral domain \\
  $F$ is a commutative ring with unity $1\ne0$

  Assume $a\in F,a\ne0$ \\
  Let $L_a:F\to F$ be defined by $L_a(x)=ax$

  Assume $L_a(x)=L_a(y)$ \\
  $ax=ay$ \\
  But $F$ is an integral domain, so the cancellation laws hold \\
  $x=y$ \\
  $\therefore L_a$ is one-to-one.

  But $F$ is finite, so $L_a$ is also onto \\
  $\therefore L_a$ is a bijection on $F$.

  $1\in F$ \\
  $\exists\,x\in F,L_a(x)=1$ \\
  $ax=1$ \\
  But $F$ is cummutative so $xa=1$ \\
  So $x$ is a multiplicative inverse for $a$ \\
  Thus every non-zero element of $F$ has a multiplicative inverse

  $\therefore F$ is a field.
\end{theproof}

\begin{corollary}
  $p$ prime $\implies\Z_p$ is a field.
\end{corollary}

\end{document}
