\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Homework \#4
\end{center}

\vspace{0.5in}

\underline{Reading}

Please read sections 2.1 through 2.7 and do all concept problems in the posted
sections on web\-assign.

\underline{Problems}

State all domains in interval notation!

\begin{enumerate}
\item Consider the function:
\[y=-\sqrt[3]{x-5}+1\]
\begin{enumerate}
\item List the transformations, starting from a basic function.
\item Determine any x-intercepts.
\item Determine any y-intercepts.
\item Sketch a graph of the function.
\item Determine the domain of the function.
\item Determine the range of the function.
\item On which intervals is the function increasing?
\item On which intervals is the function decreasing?
\end{enumerate}

\bigskip

\item Let:
\[f(x)=\sqrt{x}(x+1)\]
\[g(x)=\sqrt{x}\]
\begin{enumerate}
\item Determine $f+g$ and state the domain.
\item Determine $fg$ and state the domain.
\item Determine $\frac{f}{g}$ and state the domain.
\item Determine $\frac{f}{f}$ and state the domain.
\end{enumerate}

\bigskip

\item Let:
\[h(x)=\sqrt[3]{\frac{x+1}{x-1}}-5\]
Find a suitable $f(x)$ and $g(x)$ such that $h=f\circ g$. Remember, neither is
allowed to be just $x$. Be careful to correctly determine which is the inner
function and which is the outer function.

\bigskip

\item Let:
\[f(x)=\frac{1}{x}\]
Compute the difference quotient $\frac{f(x+h)-f(x)}{h}$

\bigskip

\item A certain chemical reaction proceeds at a linear pace with 4kg of product
being produced every 30 seconds. At the start of the reaction there was already
2kg of product existing.
\begin{enumerate}
\item Express the amount of product at time $t$ (starting at $t=0$) by a linear
equation: $p(t)=At+B$.
\item What does $A$ represent?
\item What does $B$ represent?
\item How much product is there after 15 seconds?
\end{enumerate}

\end{enumerate}
\end{document}
