\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{tikz}
\renewcommand{\l}{\lambda}
\pagestyle{plain}
\begin{document}

\begin{center}
  \large
  Math-71 Sections 9, 11, 12

  \Large
  Homework \#10 Solutions
\end{center}

\subsection*{Problem}

You work for a large conglomerate of 100 associated companies.  In order to avoid antitrust issues with the DOJ, you need
to divide the 100 companies into 4 different groups such that:
\begin{enumerate}
\item Companies within the same group cannot do business with each other.
\item Companies in different groups can do business with each other.
\end{enumerate}
What organization of the 100 companies into the 4 groups maximimizes the number of business opportunities?

\begin{enumerate}[label={\alph*)}]
\item Start by labeling the groups \(X\), \(Y\), \(Z\), and \(W\).  Let \(x=\) the number of companies assigned to group \(X\)
  and so on for the other groups.  Construct an equation in \(x\) for the number of business opportunities for a company in
  group \(X\) --- i.e., how many companies can that company do business with?
  \[100-x\]
\item Now build an equation in \(x\) for the total number of business opportunities for all companies in group \(X\).
  \[x(100-x)\]
\item Do likewise for the remaining groups and construct a function \(f(x,y,z,w)\) that gives the total number of business
  opportunities across all the groups.
  \[f(x,y,z,w)=x(100-x)+y(100-y)+z(100-z)+w(100-w)\]
\item What is the constraint on \(x\), \(y\), \(z\), and \(w\)?
  \[x+y+z+w=100\]
\item Introduce a Lagrange multiplier \(\l\) and determine \(f_x=\l g_x\), where \(g\) is the function constructed from the
  above constraint.
  \begin{gather*}
    f_x=100-2x \\
    g_x=1 \\
    \\
    100-2x=\l
  \end{gather*}
\item Do likewise for \(f_y\), \(f_z\), and \(f_w\), and combine them with the constraint so that you have 5 equations in
  5 unknowns.
  \begin{gather*}
    100-2x=\l \\
    100-2y=\l \\
    100-2z=\l \\
    100-2w=\l \\
    x+y+z+w=100
  \end{gather*}    
\item Use substitution to determine a value for \(\l\).
  \begin{gather*}
    x=\frac{1}{2}(100-\l)=50-\frac{\l}{2} \\
    y=50-\frac{\l}{2} \\
    z=50-\frac{\l}{2} \\
    w=50-\frac{\l}{2} \\
    \\
    (50-\frac{\l}{2})+(50-\frac{\l}{2})+(50-\frac{\l}{2})+(50-\frac{\l}{2})=100 \\
    4(50-\frac{\l}{2})=100 \\
    50-\frac{\l}{2}=25 \\
    \frac{\l}{2}=25 \\
    \l=50
  \end{gather*}
\item Substitute the value for \(\l\) into the other equations to determine the optimal distribution of companies into the
  4 groups.
  \begin{gather*}
    x=50-\frac{50}{2}=50-25=25 \\
    y=25 \\
    z=25 \\
    w=25
  \end{gather*}
  Thus, the best allocation is an even allocation among the groups:
  \[x=y=z=w=25\]
\end{enumerate}

\end{document}
