\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{siunitx}
\pagestyle{plain}
\renewcommand{\o}{\theta}
\newcommand{\w}{\omega}
\newcommand{\p}{\phi}
\begin{document}

\begin{center}
\Large Math-19 Exam \#5
\end{center}

\vspace{0.5in}

Name: \rule{4in}{1pt}

\vspace{0.5in}

This exam is closed book and notes. You may use a calculator; however, no cell
phones or tablets are allowed. Show all work; there is no credit for guessed
answers. All values should be exact with no decimals unless you are
specifically asked for an approximate or decimal answer. Be careful to check
for extraneous solutions.

\vspace{0.5in}

\begin{center}
  \scalebox{2}{
    \begin{tabular}{|c|c|}
      \hline
      problem & score \\
      \hline
      1 & \hspace{0.5in} \\
      \hline
      2 & \\
      \hline
      3 & \\
      \hline
      4 & \\
      \hline
      5 & \\
      \hline
      6 & \\
      \hline
      7 & \\
      \hline
      8 & \\
      \hline
      9 & \\
      \hline
      10 & \\
      \hline
      TOTAL & \\
      \hline
    \end{tabular}}
\end{center}

\newpage

\begin{enumerate}

\item Consider the angle $\o=-42^{\circ}$.
  \begin{enumerate}
  \item Convert to radians (leave the answer reduced and in terms of $\pi$).

    \vspace{2in}

  \item Find a coterminal angle in the interval $[0,2\pi]$.
  \end{enumerate}

  \newpage
  
\item Consider the trigonometric function:
  \[f(t)=-2\cos\left(2t+\frac{\pi}{3}\right)\]
  \begin{enumerate}
  \item What is the amplitude?

    $A=$

  \item What is the angular frequency?

    $\w=$

  \item What is the period?

    $T=$
    
  \item What is the horizontal translation?

    $b=$\hspace{1in}to the:
    
  \item What is the phase angle?

    $\p=$

  \item Sketch one period of the graph from $[b,b+T]$. Be sure to label the
    four key $t$ values and use dotted lines to indicate the amplitude.

    \begin{tikzpicture}
      \draw (-5,0) -- (5,0);
      \draw (0,-5) -- (0,5);
    \end{tikzpicture}
  \end{enumerate}

  \newpage

\item Consider the trigonometric function:
  \[f(t)=2\tan\left[2\pi\left(t-\frac{1}{4}\right)\right]\]
  \begin{enumerate}
  \item What is the angular frequency?

    $\w=$

  \item What is the period?

    $T=$
    
  \item What is the horizontal translation?

    $b=$\hspace{1in}to the:
    
  \item Sketch one period of the graph from
    $\left(b-\frac{T}{2},b+\frac{T}{2}\right)$. Be sure to show the asymptotes
    at the ends of the interval and label the zero.

    \vspace{0.25in}

    \begin{tikzpicture}
      \draw (-5,0) -- (5,0);
      \draw (0,-5) -- (0,5);
    \end{tikzpicture}
  \end{enumerate}

  \newpage

\item Evaluate the following expressions:
  \[\cos^{-1}\left(\cos\frac{2\pi}{3}\right)\]

  \vspace{2in}

\item Evaluate the following expressions:
  \[\sin\left(\tan^{-1}\frac{1}{2}\right)\]

  \vspace{2in}

\item Rewrite the following expression in terms of $x$:
  \[\tan\left(\cos^{-1}\frac{x}{\sqrt{1-x^2}}\right)\]

  \newpage

\item A car has $\SI{12}{in}$ tires that are rotating at $\SI{800}{rpm}$.
  Assuming no slippage between the tires and the road, how fast is the car
  traveling (in mph)?

  \vspace{4in}

\item A plane passes directly over a control tower. A radar sensor that is
  located $\SI{500}{ft}$ from the tower determines that the angle of
  elevation to the plane is $72^{\circ}$. What is the elevation of the plane
  (to the nearest foot)?

  \newpage

\item Two observers on shore are $\SI{1000}{ft}$ apart and are viewing a
  ship on the water according to the following diagram:

  \vspace{0.25in}

  \begin{center}
    \begin{tikzpicture}
      \node [draw,circle] (a) at (0,-2) {$P_1$};
      \node [draw,circle] (b) at (0,4) {$P_2$};
      \node [draw,circle] (c) at (5,0) {ship};
      \draw [dashed] (a) to (b);
      \draw [dashed] (a) to (c);
      \draw [dashed] (b) to (c);
      \node at (0.75,-1.25) {$60^{\circ}$};
      \node at (0.75,2.75) {$45^{\circ}$};
    \end{tikzpicture}
  \end{center}

  How far is the ship from person 1 (to the nearest foot)?

  \newpage

\item A particle undergoes damped harmonic motion in one dimension about the
  equilibrium position $x=0$. Let $x(t)$ denote the particle's position at
  time $t$. At $f(0)=5$ the particle is at its right-most position for the
  first cycle. At $f(1)=-4$ the particle is at its left-most position for the
  first cycle. Recall that the equation for this type of motion is:
  \[f(t)=Ae^{-kt}\cos\w t\]
  \begin{enumerate}
  \item Identify the following values:
    \[A=\]
    \[T=\]
    \[\w=\]
  \item Calculate $k$. Round your answer to two significant digits.
  \end{enumerate}

\end{enumerate}

\end{document}
