\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{siunitx}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-8 Practice Exam \#2
\end{center}

\vspace{0.5in}

\newcommand{\fillin}{\rule[-10pt]{3in}{1pt}}
\newcommand{\sfillin}{\rule[-10pt]{0.5in}{1pt}}

\begin{enumerate}
\item Identify the following:

  \begin{tabular}{ll}
    \\
    $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$ & \fillin \\
    \\
    $D=b^2-4ac$ & \fillin \\
    \\
    $ax^2+bx+c=0$ & \fillin
  \end{tabular}

  \bigskip

\item Muri is a shopkeeper that specializes in pickled vegetables. She has
  determined over the years that the best brine (salt solution) for pickling
  vegetables is 2 kg of salt per liter of water (2 kg/L).  One day, she has her
  not-so-bright nephew helping her and he uses too much salt, resulting in
  a 5 kg/L solution.  If her nephew made up 10 liters of the too-salty solution,
  how much pure water must he add to it to get the ideal 2 kg/L solution?

  \newpage

\item Solve for $x$ by completing the square:
  \[3x^2+5x-2=0\]

  \vspace{3in}

\item Solve the same equation using the quadratic formula.

  \vspace{3in}

\item Using the results from the previous two problems, state a factorization for the
  original quadratic equation. You must use the previous results for full credit.

  \newpage

\item Solve the following:
  \begin{enumerate}
  \item Solve for $x$. State you answer both graphically and using setbuilder notation:
    \[\abs{3x-2}-1=5\]

    \vspace{2in}
    
  \item Solve for $x$. State you answer graphically, using interval notation, and
    using interval notation.
    \[\abs{3x-2}-1\le5\]
    
    \vspace{2in}
    
  \item Solve for $x$. State you answer graphically, using interval notation, and
    using interval notation.
    \[\abs{3x-2}-1>5\]
  \end{enumerate}

  \newpage
  
\item We discussed in class the four possibilities of a discriminant and how they
  predict the number and type of solutions to the corresponding quadratic equation.
  List the four cases, including discriminant value, number of solutions, and type of
  solutions.

  \bigskip

  \begin{tabular}{ccc}
    D & COUNT & TYPE \\
    \\
    \sfillin & \sfillin & \fillin \\
    \\
    \sfillin & \sfillin & \fillin \\
    \\
    \sfillin & \sfillin & \fillin \\
    \\
    \sfillin & \sfillin & \fillin
  \end{tabular}

  \vspace{0.5in}

\item Solve for $x$;
  \[x^4+5x^2-24=0\]

  \newpage

\item Solve for $x$:
  \[(x-2)^{\frac{3}{4}}-27=0\]

  \newpage

\item Solve for $x$, stating your answer in interval notation. A full credit answer
  includes the work that shows a graphical representation and a sign table.
  \[\frac{x^2(2-x)(x+2)}{(4+x)(5-x)^2}\le0\]
\end{enumerate}

\end{document}
