\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\renewcommand{\a}{\alpha}
\renewcommand{\l}{\lambda}
\begin{document}
\section*{Components}

\begin{definition}[Component]
  Let \(X\) be a topological space and let \(p\in X\).  The \emph{(connected) component} of \(p\) in \(X\) is the
  union of all connected subsets of \(X\) that contain \(p\).
\end{definition}

\begin{theorem}
  Let \(X\) be a topological space.  Each component of \(X\) is connected, closed, and not contained in any
  strictly larger connected subset of \(X\).
\end{theorem}

\begin{proof}
  Assume that \(U\) is a component of \(X\) and that \(p\in U\).  By definition, \(U=\bigcup_{\a\in\l}U_{\a}\)
  where \(U_{\a}\) is a connected subset of \(X\) containing \(p\).  Now, for each \(U_{\a}\),
  \(U_{\a}\cap\set{p}\ne\emptyset\) and \(\set{p}\) is trivially connected.  Therefore \(U\) is connected.

  Assume that \(V\) is a connected component of \(X\) such that \(U\subset V\).  This means that \(p\in V\) and
  so, by definition, \(U=U\cup V\).  But this is ony true if \(V\subset U\).  Therefore \(U=V\).

  Now, since \(U\) is connected, \(\bar{U}\) is connected.  But \(p\in\bar{U}\) and so, by definition,
  \(U=U\cup\bar{U}\).  But this is only true if \(\bar{U}\subset U\).  Therefore \(U=\bar{U}\) and hence \(U\) is
  closed.
\end{proof}

\begin{theorem}
  Let \(X\) be a topological space.  The set of components of \(X\) are a partition of \(X\).
\end{theorem}

\begin{theorem}
  Let \(X\) be a topological space with a finite number of components.  The components are clopen in \(X\).
\end{theorem}

\begin{proof}
  Assume that \(X=U_1\sqcup\cdots\sqcup U_n\).  All of the \(U_k\) are closed.  But
  \(U_k=X-(U_1\sqcup\cdots\sqcup U_{k-1}\sqcup U_{k+1}\sqcup\cdots\sqcup U_n)\) is then open.  Therefore, all of the
  \(U_k\) are clopen.
\end{proof}

This result does not hold for an infinite number of components.  Consider \(Q\subset\R\) with the subspace
topology.  \(Q\) is disconnected with components \(\setb{\set{r}}{r\in\Q}\).  But \(\set{r}\) is closed and not
open.

\end{document}
