\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\usepackage{amsfonts}
\pagestyle{empty}
\begin{document}

\begin{center}
\Large Math-19 Practice Final
\end{center}

\vspace{0.25in}

\begin{enumerate}

\item You have a credit card with 36\% annual interest compounded monthly.
You use of the card over the next 3 months is summarized below:

\begin{tabular}{|c|c|c|}
\hline
MONTH & PURCHASES & PAYMENTS \\
\hline
Opening Balance & \$525 & \\
\hline
JUN & \$745 & \$500 \\
\hline
JUL & \$210 & \$600 \\
\hline
AUG & \$125 & \$150 \\
\hline
\end{tabular}

On September 1, you make an additional \$250 payment.

\begin{enumerate}
\item Who is the lender?

\item Who is the borrower?

\item Construct a polynomial in $(1+\frac{r}{n})$ that describes the account
activity right after you make the payment on Sep 1.

\item What is the account balance right after the Sep 1 payment?

\item What would be the account balance if you never did anything other than
leave the opening balance as is and the account compounds continually?
\end{enumerate}

\item Consider the function $f(x)=1+e^{-x}$.

\begin{enumerate}
\item What are the x-intercepts (if any)?

\item What are the y-intercepts (if any)?

\item What is the end behavior as $x\to\infty$?  If it is asymptotic, be sure
to state what the asymptote is, whether it is horizontal or vertical, and if
the function approaches it from above or below.

\item Repeat for $x\to-\infty$.

\item Sketch the graph of the function.  Be sure to label all intercepts and
asymptotes and show the proper end behavior.

\item What is the domain?

\item What is the range?
\end{enumerate}

\item Consider the equation $y=\log_ax$.
\begin{enumerate}
\item What is the corresponding exponential equation?

\item Derive the change of base formula.

\item Use your formula to calculate $\log_2250$.  Round your answer to 4
decimal places.

\item Does it matter if you use $\log$ or $\ln$ when using your calculator when
doing a change of base?  Why?
\end{enumerate}

\item Let $log_a100=2.36659$, $log_a3=0.56458$, and $log_a150=2.57496$.
Calculate $log_a2$ without knowing the base $a$.

\item Solve for $x$, leaving your answer as an exact value.  Points will be
deducted for approximate (decimal) answers!
\[\frac{50}{1-e^{-x}}=4\]

\item Solve for $x$, leaving your answer as an exact value.  Points will be
deducted for approximate (decimal) answers!
\[\log_9(x-5)-log_9(x+3)=1\]

\item The half-life Radium-226 is 1600 years.

\begin{enumerate}

\item Derive a base-2 equation for the radioactive decay this isotope.

\item Now derive a base-e equation.

\item You start with a 100g sample.  How much is left after 100 years?

\item How long does it take the sample to decrease to 75g?

\end{enumerate}

\item Let $\tan x=-\frac{7}{24}$ with $x$ in Quadrant IV.
\begin{enumerate}
\item Find $\sin2x$.

\item Find $\cos2x$.
\end{enumerate}

\item Rewrite in terms of $x$ and $y$ without trig functions:
$\tan(\sin^{-1}\frac{x}{2}+\cos^{-1}\frac{2y}{3})$.

\item Find all possible solutions for $\theta$:
\[\sqrt{8}\sin{x}\cos{x}+\sqrt{6}\sin{x}-2\cos{x}-\sqrt{3}=0\]

\end{enumerate}

\end{document}
