\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-1003b Homework \#1
\end{center}

\vspace{0.5in}

\underline{Reading}

\bigskip

\begin{itemize}
\item Really focus on your lecture notes for the information on rational
  numbers.
\item Review textbook chapters 1, 2, and 5.
\item Text book sections 7.1 and 7.2.
\end{itemize}

\bigskip

\underline{Problems}

\bigskip

\begin{enumerate}
\item Questions about rational numbers. Be sure to explain why a statement is
  either true or false. Provide and explain counterexamples for all false
  statements.
  \begin{enumerate}
  \item Describe the three forms of a rational number covered in class and give
    an example of each.

  \item Is zero a rational number?

  \item Is $\frac{\sqrt{9}}{2}$ a rational number?

  \item Is every fraction a rational number?

  \item Based on the class discussion of rational numbers (i.e., the meaning
    of $\frac{p}{q}$ on the number line), explain why zero can never appear in
    the denominator.
  \end{enumerate}

\vspace{0.5in}

\item Consider the numbers $120$ and $252$.
  \begin{enumerate}
  \item State the prime factorization for each.
  \item Show how to determine and then state their least common multiple (LCM).
  \item Show how to determine and then state their greatest common denominator
    (GCD).
  \item Show how to simplify $\frac{120}{252}$ using the above information.
  \end{enumerate}

\vspace{0.5in}

\item Rewrite $4-9x^2$ by factoring out $(-3x)$.

\newpage

\newcommand{\rea}{\frac{2x^2+5x+2}{x^2-3x}}
\newcommand{\reb}{\frac{2x^3+4x^2}{x^2-9}}

\item Operations on rational expressions:
  \begin{enumerate}
  \item Fully factor:
    \[\rea\]
  \item Fully factor:
    \[\reb\]
  \item Determine and fully simplify:
    \[\rea\cdot\reb\]
  \item Determine and fully simplify:
    \[\rea\div\reb\]
  \end{enumerate}
\end{enumerate}
\end{document}
