\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{url}
\pagestyle{plain}
\begin{document}

\begin{center}
  \emph{San Jos\'{e} State University}

  Fall 2017

  \Large{Math-19 (Precalculus)}\normalsize

  Section 01 \\
  MTWRF 9:00am--9:50am \\
  Sweeney Hall 347
\end{center}

\vspace{0.5in}

\begin{description}

\item[Instructor:] Jeffery Cavallaro (\url{jeffery.cavallaro@sjsu.edu})

\item[Office:] Duncan Hall 209 (the TA room)

\item[Office Hours:] TR 10:00am--12:00pm

\item[Text:] \emph{Precalculus}, Stewart, Redlin, and Watson, $7^{th}$ ed. You
  must have the correct edition. Bring your book to class. The eBook version
  is OK, but make sure that you have a way to access it during class.

\item[Web:] We will use both canvas and WebAssign. All class communications,
  including reading assignments, homework assignments, helpful resource
  documents, and grades are via canvas (\url{sjsu.instructure.com}). WebAssign
  (\url{WebAssign.com}) will be used for a portion of the homework (see below).
  Once you are registered for the course you should be able to see the course
  listed on your canvas account. Each student must purchase a Web\-Assign
  license. Note that the ``enhanced'' license is not required; however, you
  may find the extra teaching materials that it provides helpful. The
  WebAssign class code will be distributed on the first day of class and via
  a canvas announcement. Once you register your license, you will need this
  class code to access the class.

\item[Calculator:] You are required to have a TI-84+ (silver edition or CE) calculator.
  If you are buying a new one, I suggest the TI-84 Plus CE. I have \emph{no}
  problem with you checking your homework and exam answers using your calculator --- in
  fact, I encourage it; however, answers with no supporting work will receive absolutely
  no credit. \emph{No other scientific calculators, cell phones, tablets, or computers
    are allowed in lieu of a TI-84+ calculator!} You must also have a USB data cable
  to connect your calculator to your PC or MAC and the TI Connect CE software installed
  on your computer --- you will be turning in screenshots as part of your homework.

\item[Learning Objectives:] We will start by reviewing the real number system, algebraic
  expressions, and algebraic equations. We will then take a detailed look at functions
  and study various types of functions (polynomials, exponential, trigonometric) using
  data, equations, and graphs. We will conclude with some analytical geometry, with an
  emphasis on trigonometry and conic sections. The overall goal is to provide you with
  all the tools needed for calculus and to develop some mathematical sophistication
  (walk the walk and talk the talk).

\item[Attendance:] I will not take attendance after the first week; however, it is
  vitally important that you come (on time, for our time is limited) to every class. The
  book has more information than we could possibly cover, so I will highlight in class
  what is important. I will also enhance certain subjects that I feel are important for
  your calculus preparation. Bring your book and calculator to every class meeting. If
  you miss a class, it is your responsibility to talk to your peers and find out what
  you missed --- don't ask me to repeat a lecture during office hours.

\item[Time:] You will need to spend a \emph{minimum} of 15 hours per week outside of
  class doing homework and studying. This class is \emph{very} intensive and will
  require disciplined study habits.

\item[Holidays:] Class will not meet on Mon, 9/4 (Labor Day), Fri 11/10 (Veterans' Day),
  and 11/22-11/24 (Thanksgiving Break).

\item[Reading:] Reading from the textbook will be assigned each Friday for the material
  to be covered in the coming week. Please read everything, not just the stuff in the
  boxes, prior to lecture. Make sure that you can work all of the example problems prior
  to attempting any homework problems.

\item[WebAssign Homework:] The web-based homework will be submitted via WebAssign.
  Web\-Assign requires that you format your answers with math symbols using an answer
  tool. Don't get frustrated! It may take a couple times for you to get the hang of it;
  it will get easier the more you use it. The problems assigned on WebAssign are even
  problems from the book. WebAssign homework will be assigned on Monday and will be due
  on the following Sunday at 11:59pm (midnight). There are \emph{no} extensions, so
  please do not fall behind.

\item[Written Homework:] Written homework will be passed out in class on Monday (and
  posted on canvas) and will be due the following Monday at the start of class. There
  will be 16 homework assignments (one each week). Late homework will not be accepted;
  however, I will drop your lowest two scores. See \emph{Homework Rules} for more
  information.

\item[Exams:] There will be five, non-cumulative exams, tentatively scheduled for the
  following Fridays: 9/15, 10/6, 10/27, 11/17, and 12/8. \emph{You must plan to take the
    exams at their scheduled times}. In particular, previous travel arrangements are
  \emph{not} a valid excuse to miss an exam. All exams are closed book and notes. Your
  calculator and a double-sided $4\times6$ note card are allowed.

\item[Final:] The last day of class is Monday, 12/11. The final exam is cumulative and
  occurs on Monday, 12/18, 7:15--9:30am. All above exam policies apply to the final as
  well.

  \newpage

\item[Grading:]  Your semester grade is determined as follows:

  \bigskip

  \begin{minipage}{3in}
    \begin{tabular}{|c|c|}
      \hline
      WebAssign Homework & 25\% \\
      \hline
      Written Homework & 25\% \\
      \hline
      Exams & 25\% \\
      \hline
      Final Exam & 25\% \\
      \hline
    \end{tabular}
  \end{minipage}
  \begin{minipage}{3in}
    \begin{tabular}{|c|c|}
      \hline
      A+ & 97--100 \\
      \hline
      A & 93--96 \\
      \hline
      A- & 90--92 \\
      \hline
      B+ & 87--89 \\
      \hline
      B & 83--86 \\
      \hline
      B- & 80--82 \\
      \hline
      C+ & 77--79 \\
      \hline
      C & 70--76 \\
      \hline
      NC & 0--69 \\
      \hline
    \end{tabular}
  \end{minipage}
  
\item[Credit:] A grade of C or better meets the \emph{Area B4: Mathematical Concepts} GE
  requirement. A grade of C or better is required for placement into Math 30P. A grade
  of B or better is required for placement into Math 30.

\item[Tutoring:] Peer tutoring is available to all SJSU students, free of charge, from
  the PeerConnections center. See \url{http://peerconnections.sjsu.edu} for more
  information.

\item[Academic integrity:] Your commitment to learning (as shown by your enrollment at
  SJSU) and SJSU's Academic Integrity Policy require you to be honest in all of your
  academic course work.  Faculty are required to report all infractions to the Office of
  Student Conduct and Ethical Development. See \url{http://www.sjsu.edu/studentconduct}
  for more information.

\item[Disabilities:] If you need course adaptations or accommodations due to a
  disability, or if you need special arrangements in case the building must be
  evacuated, please make an appointment with me as soon as possible, or see me during
  office hours. All students with disabilities must register with the Accessible
  Education Center (AEC) to establish a record of their disability. See
  \url{http://www.sjsu.edu/aec} for more information.

\end{description}

\end{document}
