\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\begin{document}
\section*{Ring Isomorphisms}

\begin{definition}
  Let $R$ and $R'$ be rings. To say that $\phi:R\to R'$ is a \emph{ring isomorphism}
  means:
  \begin{enumerate}
  \item $\phi$ is a bijection
  \item $\phi$ is a ring homomorphism
  \end{enumerate}
  If so, then $R$ and $R'$ are said to be isomorphic, denoted $R\simeq R'$.
\end{definition}

\begin{lemma}
  Let $\phi:R\to R'$ be an isomorphism of rings. $\phi^{-1}:R'\to R$ exists and is also an
  isomorphism of rings.
\end{lemma}

\begin{theproof}
  $\phi$ is bijective, so $\phi^{-1}$ exists and is bijective

  Assume $x,y\in R'$ \\
  $\exists\,a\in R,\phi(a)=x$ \\
  $\exists\,b\in R,\phi(b)=y$

  $\phi^{-1}(x)=a$ \\
  $\phi^{-1}(y)=b$

  $\phi^{-1}(x+y)=\phi^{-1}(\phi(a)+\phi(b))=\phi^{-1}(\phi(a+b))=(\phi^{-1}\phi)(a+b)=
  a+b=\phi^{-1}(x)+\phi^{-1}(y)$

  $\phi^{-1}(xy)=\phi^{-1}(\phi(a)\phi(b))=\phi^{-1}(\phi(ab))=(\phi^{-1}\phi)(ab)=
  ab=\phi^{-1}(x)\phi^{-1}(y)$
\end{theproof}

\begin{lemma}
  Let $\phi:R\to R'$ and $\mu:R'\to R''$ be isomorphisms of rings.
  $\mu\phi:R\to R''$ is also an isomorphism of rings.
\end{lemma}

\begin{theproof}
  Assume $(\mu\phi)(a)=(\mu\phi)(b)$ \\
  $\mu(\phi(a))=\mu(\phi(b))$ \\
  $\mu$ is a bijection, so $\mu^{-1}$ exists \\
  $\phi(a)=\phi(b)$ \\
  $\phi$ is a bijection, so $\phi^{-1}$ exists \\
  $a=b$ \\
  $\therefore \mu\phi$ is one-to-one.

  Assume $z\in R''$ \\
  $\exists\,y\in R',\mu(y)=z$ \\
  $\exists\,x\in R,\phi(x)=y$ \\
  $(\mu\phi)(x)=\mu(\phi(x))=\mu(y)=z$ \\
  $\therefore \mu\phi$ is onto, and thus a bijection.

  Assume $a,b\in R$

  $(\mu\phi)(a+b)=\mu(\phi(a+b))=\mu(\phi(a)+\phi(b))=\mu(\phi(a))+\mu(\phi(b))=
  (\mu\phi)(a)+(\mu\phi)(b)$

  $(\mu\phi)(ab)=\mu(\phi(ab))=\mu(\phi(a)\phi(b))=\mu(\phi(a))\mu(\phi(b))=
  (\mu\phi)(a)(\mu\phi)(b)$

  $\therefore \mu\phi$ is a homomorphism, and thus an isomorphism.
\end{theproof}

\begin{theorem}
  Isomorphism is an equivalence relation.
\end{theorem}

\begin{theproof}
  \listbreak
  \begin{description}
  \item Reflexive: Assume $R$ is a ring

    Let $\phi=\iota_R$ \\
    $\iota_R$ is a ring isomorphism on $R$ \\
    $\therefore R\simeq R$

  \item Symmetric: Assume $R\simeq R'$

    There exists ring isomorphism $\phi:R\to R'$ \\
    So there exists ring isomorphism $\phi^{-1}:R'\to R$ (lemma) \\
    $\therefore R'\simeq R$

  \item Transitive: Assume $R\simeq R'$ and $R'\simeq R''$

    There exists ring isomorphism $\phi:R\to R'$ \\
    There exists ring isomorphism $\mu:R'\to R''$ \\
    So there exists ring isomorphism $\mu\phi:R\to R''$ (lemma) \\
    $\therefore R\simeq R''$
  \end{description}
\end{theproof}

\end{document}
