\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\usepackage{mathtools}
\pagestyle{plain}
\begin{document}

\begin{center}
\Large Math-19 Homework \#2
\end{center}

\vspace{0.5in}

\underline{Reading}

Please read sections 1.1 through 1.5 and 1.7 and then do all concept problems
in the posted sections on web\-assign.

\underline{Problems}

\begin{enumerate}
\item Simplify completely. Your answer should have no negative exponents and
please rationalize the denominator. Don't worry if the exponents get messy.
\[\frac{\sqrt[4]{\sqrt{75}+\sqrt{27}}}{\sqrt{4\sqrt{20}\sqrt[3]{54}}}\]

\item A student writes the following statements. Determine if each is either
correct or incorrect (or misleading). Explain why incorrect statements are
incorrect.
\begin{enumerate}
\item $\sqrt{9}=\pm3$
\item $\left(x^{\frac{1}{2}}\right)^2=\abs{x}$
\item $\left(x^2\right)^{\frac{1}{2}}=x$
\item $\left(x^3\right)^{\frac{1}{3}}=\abs{x}$
\end{enumerate}

\item Solve for $x$ by \emph{completing the square}.
\[2x^2+4x-3=0\]

\item A man stands atop a $256ft$ cliff with a  ball.
\begin{enumerate}
\item How long does it take for the ball to hit the ground if he simply
releases the ball?

\item How long does it take for the ball to hit the ground if he throws the
ball up with a velocity of $16 ft/s$?

\item How long does it take for the ball to hit the ground if he throws the
ball down with a velocity of $16 ft/s$? (Hint: no additional calculations are
needed).

\item Assume that a lady is standing on the ground below the cliff and throws
a ball up so that it passed the man on the cliff at a velocity of $16 ft/s$.
How long would it be before the ball hits the ground? (Hint: you already have
all the information that you need).
\end{enumerate}

\newpage

\item Muri is a shopkeeper that specializes in pickled vegetables. She has
determined over the years that the best brine (salt solution) for pickling
vegetables is 2 kg of salt per liter of water (2 kg/L).  One day, she has her
not-so-bright nephew helping her and he uses too much salt, resulting in
a 5 kg/L solution.  If her nephew made up 10 liters of the too-salty solution,
how much pure water must he add to it to get the ideal 2 kg/L solution? For
full credit, show the mixture equation and the appropriate values for each
concentration and volume value in the equation.
\end{enumerate}
\end{document}
