\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{plain}

\renewcommand{\implies}{\rightarrow}
\renewcommand{\iff}{\leftrightarrow}

\begin{document}

\begin{center}
  \large Math-42 Worksheet \#3

  \textbf{Propositional Equivalences}
\end{center}

\vspace{0.5in}

\begin{enumerate}[left=0in,itemsep=0.5in]
\item Using truth tables, show that implication is left distributive:
  \begin{gather*}
    p\implies(q\land r)\equiv(p\implies q)\land(p\implies r) \\
    p\implies(q\lor r)\equiv(p\implies q)\lor(p\implies r)
  \end{gather*}
\item Using truth tables, show that implication is \emph{not} right distributive.
\item What are the correct equivalences for right distributivity?

\item Prove that \(\lnot(p\implies q)\equiv p\land\lnot q\) using:
  \begin{enumerate}
  \item A truth table.
  \item Logical equivalences (hint: implication equivalence and deMorgan).
  \end{enumerate}

\item Negate each of the following compound propositions:
  \begin{enumerate}
  \item Jack goes to school and he gets good grades.
  \item If Jack goes to school then he will get good grades.
  \item If Jack goes to school and gets good grades then he will get a good job.
  \item Jack goes to school or gets a good job.
  \end{enumerate}

\item Prove that \([\lnot p\land(p\lor q)]\implies q\) is a tautology using:
  \begin{enumerate}
  \item A truth table.
  \item Logical equivalences.
  \end{enumerate}

\item Prove that \(p\oplus q\) is equivalent to \(\lnot(p\iff q)\) using:
  \begin{enumerate}
  \item A truth table.
  \item Logical equivalences.
  \end{enumerate}

\item Consider the following logical equation
  \[(p\land q)\land(p\iff r)\land(r\lor p\implies q)\land(s\implies\lnot r)\land s\]
  Without using a truth table (and you wouldn't want to), determine whether the logical equation is satisfiable.
\end{enumerate}

\end{document}
