\documentclass[letterpaper,12pt,fleqn]{article}
\usepackage{matharticle}
\pagestyle{empty}
\newcommand{\p}{\pi}
\newcommand{\B}{\mathcal{B}}
\newcommand{\T}{\mathscr{T}}
\newcommand{\e}{\epsilon}
\renewcommand{\a}{\alpha}
\renewcommand{\b}{\beta}
\renewcommand{\l}{\lambda}
\begin{document}
\section*{Product Spaces}

\begin{definition}[Projection]
  Let \(X\) and \(Y\) be sets.  The \emph{projection} functions \(\p_X:X\times Y\to X\) and \(\p_Y:X\times Y\to Y\)
  are defined by:
  \begin{align*}
    \p_X(x,y) &= x \\
    \p_Y(x,y) &= y
  \end{align*}
\end{definition}

\begin{definition}[Product Topology]
  Let \(X\) and \(Y\) be topological spaces.  The \emph{product topology} on the product \(X\times Y\) is the
  topology with basis \(\B\) given by:
  \[\B=\setb{U\times V}{U\in\T_X\ \text{and}\ V\in\T_Y}\]
\end{definition}

\begin{theorem}
  The basis for a product topology is in fact a basis.
\end{theorem}

\begin{proof}
  Assume that \(X\) and \(Y\) are topological spaces and let:
  \[\B=\setb{U\times V}{U\in\T_X\ \text{and}\ V\in\T_Y}\]

  Assume that \((a,b)\in X\times Y\).  Since \(a\in X\), there exists \(U\in\T_X\) such that \(a\in U\).  Likewise,
  since \(b\in Y\), there exists \(V\in\T_Y\) such that \(b\in V\).  Therefore, \((a,b)\in U\times V\in\B\).

  Now, assume that \(U_1\times V_1,U_2\times V_2\in\B\) and assume that \((a,b)\in U_1\times V_1\cap U_2\times V_2\).
  This means that \(a\in U_1\cap U_2\) and \(b\in V_1\cap V_2\).  But \(U_1\) and \(U_2\) are generated by basic
  sets in \(\T_X\), and \(V_1\) and \(V_2\) are generated by basic sets in \(\T_Y\).  So there exists basic sets
  \(W_1\in\T_X\) and \(W_2\in\T_Y\) such that \(a\in W_1\subset U_1\cap U_2\) and \(b\in W_2\subset V_1\cap V_2\).
  Therefore, \(W_1\times W_2\in\B\) and \((a,b)\in W_1\times W_2\subset U_1\times V_1\cap U_2\times V_2\).

  Therefore \(\B\) is a basis for a topology on \(X\times Y\).
\end{proof}

\begin{theorem}
  Let \(X,Y\) be topological spaces.  If \(A\subset X\) and \(B\subset Y\) are closed sets then \(A\times B\)
  is closed in \(X\times Y\).
\end{theorem}

\begin{proof}
  Since \(A\) and \(B\) are closed, \(X-A\) and \(Y-B\) are open.  And so:
  \[(X-A)\times(X-B)=(X\times Y)-(A\times B)\]
  is open.  Therefore \(A\times B\) is closed.
\end{proof}

\begin{theorem}
  Let \(X\) and \(Y\) be topological spaces.  The product topology on \(X\times Y\) is the same as the topology
  generated by the subbasis of inverse images of open sets under the projection functions, that is, the basis is
  given by:
  \[\B=\setb{\p_X^{-1}(U)}{U\in\T_X}\cup\setb{\p_Y^{-1}(V)}{V\in\T_Y}\]
\end{theorem}

\begin{proof}
  Assume \(U\in\T_X\) and \(V\in\T_y\):
  \begin{gather*}
    \p_X^{-1}(U)=\setb{(x,y)}{x\in U,y\in Y}=U\times Y \\
    \p_Y^{-1}(V)=\setb{(x,y)}{x\in X,y\in V}=X\times V \\
    \\
    \p_X^{-1}(U)\cap\p_Y^{-1}(V)=(U\times Y)\cap(X\times V)=(U\cap X,V\cap Y)=(U,V)
  \end{gather*}
\end{proof}

\begin{example}
  The standard topology on \(\R^2\) is not the same as the product topology on \(\R\times\R\).  The basic open sets
  in the standard topology are the open balls \(B(p,\e)\).  But these open balls can be generated in the product
  topology by arbitrary unions of basic sets of the form \((p-\e,p+\e)\times(p-\e,p+\e)\), and thus the product
  topology is finer than the standard topology.
\end{example}

\begin{notation}
  Let \(\set{X_i:i\in[n]}\) be a finite family of topological spaces:
  \[\prod_{i=1}^nX_i=X_1\times X_2\times\cdots\times X_n\]
  An element \(x=(x_1,x_2,ldots,x_n\) can be views as a function \(f:[n]\to\bigcup_{i=1}^nX_i\) where
  \(f(i)\in X_i\).
\end{notation}

\begin{definition}[Infinite Product]
  Let \(\set{X_{\a}:\a\in\l}\) be an arbitrary collection of topological spaces.  The infinite \emph{product} of
  these spaces is given by:
  \[\prod_{\a\in\l}X_{\a}=\setb{f:\l\to\bigcup_{\a\in\l}X_{\a}}{\forall\,\a\in\l,f(\a)\in X_{\a}}\]
\end{definition}

\begin{definition}
  Let \(\set{X_{\a}:\a\in\l}\) be an arbitrary collection of topological spaces and for each \(\b\in\l\) define the
  \emph{projection} function \(\p_{\b}:\prod_{\a\in\l}X_{\a}\to X_{\b}\) by \(\p_{\b}(f)=f(\b)\).  The
  \emph{product topology} on \(\prod_{\a\in\l}X_{\a}\) is the one generated by the subbasis of sets of the form
  \(\p_{\b}^{-1}(U_{\b})\) where \(U_{\b}\in\T_{X_{\b}}\).
\end{definition}

\begin{example}
  Let \(\set{X_n:n\in\N}\) be a family of topological spaces and \(\set{U_n:n\in\N}\) be a family of sets such that
  \(U_n\in\T_{X_n}\):
  \begin{align*}
    \p_{X_1}^{-1}(U_1)\cap\p_{X_3}^{-1}(U_3)\cap\p_{X_5}^{-1}(U_4) &=
    (U_1\times X_2\times X_3\times X_4\times X_5\times\cdots)\cap \\
    & (X_1\times X_2\times U_3\times X_4\times X_5\times\cdots)\cap \\
    & (X_1\times X_2\times X_3\times U_4\times X_5\times\cdots) \\
    &= (U_1\times X_2\times U_3\times U_4\times X_5\times\cdots)
  \end{align*}
  The basis elements are the entire space except for a finite number of components.
\end{example}

\end{document}
